---
title: "cielo analyses"
author: "Hannah Lunkenheimer"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# set working directory
knitr::opts_knit$set(root.dir = '/Documents/Github/cielo')
```

```{r importing the data}
# loading packages
library(readr)

# importing the data
d_all <- read_csv("data/mergeddatafull.csv")

# now let's view our data

View(d_all)
```

## Predictions and analyses in preregistration (and more)

Question: Age as continuous

## Confirmatory analyses:
1.	Children view God as less causally relevant with age, whereas belief in God remains stable. Positive effect of religious exposure and parent interventionist beliefs on children’s causally relevant God concepts. These will interact such that children from religious families will view God as increasingly causally relevant with age. Children who perceive less control in their lives will have a more causally relevant God concept.

### Effects of age, religiosity, and control on interventionist concepts

i.	Effects of age (and religiosity*) (and control**) on interventionist concepts - child choice (explicit concept) task

1.	Multinomial logistic regression
a.	Model with all 3 above (age, relig, control) + interactions = best fit model. Put all 3 parent variables into the model and take out if not predictive. Test for multicollinearity. If yes, then Principal Components Analysis.

```{r age intervention child choice reg}


```

ii.	Effects of age (and religiosity*) (and control) on interventionist concepts – interview questions
1.	Could use linear regression if dv is sum of 4 questions. Best fit model (using AIC criterion etc)

```{r age intervention interview reg}


```

iii.	Effects of age, etc on “intervention frequency task” (Does God make..?). Would just sum number of yes responses as dv.
1.	Linear regression (+histogram of each question. Factor analysis to determine clusters)

```{r age intervention task reg}


```

iv.	Effects of age on God real/pret (we can use kids who said pretend to get a general sense of God belief in our larger sample)
1.	Binomial logistic regression

```{r age god real reg}


```

v.	Effects of age on God certainty in our study sample
1.	Binomial logistic regression

```{r age god certainty reg}


```

### Exploratory analyses: Qualitative responses to interview questions. 
Also include here an analysis of what types of things kids think God does (intervention frequency task).

1.  Factor analysis on “Does God..?” (intervention frequency) task. Then analyze whether the factors differ and differ by age
	a. dv is continuous so repeated measures ANOVA with age group as iv (I don’t know how to do repeated measures if age is continuous – is there a repeated measure regression?)
	b. add parent/relig questions to this?
	
```{r intervention freq FA}


```

2. Number and percent of each explanation type to assess whether we need to collapse categories – probably around 5 is ideal and we have more than that. Then collapse if we need to and calculate percentage of children’s responses in each category as a function of age and parent concepts/religiosity. Make graphs of these. 
	a. logistic regression to assess effects of category type and interactions with age and religiosity (used this in W&C) – is dv proportion or number?
	b. need to compute reliability (Cohen’s Kappa in SPSS)
	
```{r log reg}


```
