---
title: "cielo analyses"
author: "Hannah Lunkenheimer"
date: "`r Sys.Date()`"
output: html_document
---

# Cielo Analyses Checklist

This document serves as a reference for the analyses we want to do for Cielo. Each will have a 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# set working directory
knitr::opts_knit$set(root.dir = '/Documents/Github/cielo')

# Libraries 
library(tidyverse)
library(here)
library(psych)
library(nFactors)
library(lme4)
library(nlme)
library(FactoMineR)
library(sem)
library(ggplot2)
library(dplyr)
library(lavaan) # for factor analysis 
library(performance) # for model performance
library(texreg)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(lattice)
library(readr)

```



```{r importing the data}
# importing the data
d_all <- read_csv("data/Cielo1_MergedFull_practice.csv")

# now let's view our data
#View(d_all)

# some participant data needs to be thrown out completely according to the red rows in our CSV file, so let's remove those participants completely here (ID 129, 152, 175, and 277)
subset(d_all, id_num != "129" & id_num != "152" & id_num != "175" & id_num != "277")
# great, we've removed our 4 participants completely from our dataframe d_all and now have all of the participants we can use for analyses
```

```{r selecting practice items}

# here, we're creating a new dataframe for a subset of our data that we want to look at (the practice questions)
d_practice <- d_all %>% dplyr::select(practice_dogs, practice_veg, practice_swim)

# now let's view the subset of our full data set
View(d_practice)

```

```{r descriptives practice items}

# let's look at the means, SDs, min and max for our d_practice dataframe
describe(d_practice)

#when we want to get a general idea of the responses from the dataframe, we can use the head() function for a quick look (the tibble() fuction also works for this)
head(d_practice)

# here, we're telling R which order we want the responses to be in (levels) so that our figure matches our scale. you can specify any order you want here by using ""s and what the responses are exactly. for example, if we had written "really disagree", R would not have ordered that response bc of the capitalization sensitivity

d_practice$practice_dogs = factor(d_practice$practice_dogs, levels=c("Really Disagree", "Disagree", "Kind of Disagree", "Kind of Agree", "Agree", "Really Agree"))

# let's plot the descriptive statistics with a figure using the ggplot package in our library
dog_plot <- ggplot(d_practice, aes(practice_dogs)) +
  geom_bar(fill='light blue') +
  labs(x='Scale', y="Participants", title ="Practice Question - Dogs") +
  theme_light()

# calling our figure
dog_plot

# nice!

#reordering the levels of the swim practice question
d_practice$practice_swim = factor(d_practice$practice_swim, levels=c("Really Disagree", "Disagree", "Kind of Disagree", "Kind of Agree", "Agree", "Really Agree"))

# making our ggplot
swim_plot <- ggplot(d_practice, aes(practice_swim)) +
  geom_bar(fill='purple') + 
  labs(x='Scale', y="Participants", title ="Practice Question - Swim") + 
  theme_light()

# calling our figure
swim_plot

################################
### IF YOU WANT TO PRACTICE! ###
################################

# try making your own descriptive figures from any of the variables we have access to in our cielo data. if you're having trouble remembering what the column names are, use the View() function 
```


## Predictions and analyses in preregistration (and more)

Question: Age as continuous

## Confirmatory analyses:
1.	Children view God as less causally relevant with age, whereas belief in God remains stable. Positive effect of religious exposure and parent interventionist beliefs on children’s causally relevant God concepts. These will interact such that children from religious families will view God as increasingly causally relevant with age. Children who perceive less control in their lives will have a more causally relevant God concept.

### Effects of age, religiosity, and control on interventionist concepts

i.	Effects of age (and religiosity*) (and control**) on interventionist concepts - child choice (explicit concept) task

1.	Multinomial logistic regression
a.	Model with all 3 above (age, relig, control) + interactions = best fit model. Put all 3 parent variables into the model and take out if not predictive. Test for multicollinearity. If yes, then Principal Components Analysis.

```{r age intervention child choice reg}
#downloading libraries for multinomial reg
library(foreign)
library(nnet)
```

ii.	Effects of age (and religiosity*) (and control) on interventionist concepts – interview questions
1.	Could use linear regression if dv is sum of 4 questions. Best fit model (using AIC criterion etc)

iii.	Effects of age, etc on “intervention frequency task” (Does God make..?). Would just sum number of yes responses as dv.
1.	Linear regression (+histogram of each question. Factor analysis to determine clusters)

iv.	Effects of age on God real/pret (we can use kids who said pretend to get a general sense of God belief in our larger sample)
1.	Binomial logistic regression

v.	Effects of age on God certainty in our study sample
1.	Binomial logistic regression

### Exploratory analyses: Qualitative responses to interview questions. 
Also include here an analysis of what types of things kids think God does (intervention frequency task).

1.  Factor analysis on “Does God..?” (intervention frequency) task. Then analyze whether the factors differ and differ by age
	a. dv is continuous so repeated measures ANOVA with age group as iv (I don’t know how to do repeated measures if age is continuous – is there a repeated measure regression?)
	b. add parent/relig questions to this?

2. Number and percent of each explanation type to assess whether we need to collapse categories – probably around 5 is ideal and we have more than that. Then collapse if we need to and calculate percentage of children’s responses in each category as a function of age and parent concepts/religiosity. Make graphs of these. 
	a. logistic regression to assess effects of category type and interactions with age and religiosity (used this in W&C) – is dv proportion or number?
	b. need to compute reliability (Cohen’s Kappa in SPSS)
