---
title: "child choice task-cielo"
author: "Hannah Lunkenheimer"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(moonBook)
library(dplyr)
library(readr)

# importing the data
d_all <- read_csv("data/Cielo1_MergedFull_practice.csv")

```

# Effects of age, religiosity, and control on interventionist concepts - child choice

i.	Effects of age (and religiosity*) (and control**) on interventionist concepts - child choice (explicit concept) task

1.	Multinomial logistic regression
a.	Model with all 3 above (age, relig, control) + interactions = best fit model. Put all 3 parent variables into the model and take out if not predictive. Test for multicollinearity. If yes, then Principal Components Analysis.

```{r loading data, include=FALSE}

# now let's view our data
#View(d_all)

# some participant data needs to be thrown out completely according to the red rows in our CSV file, so let's remove those participants completely here (ID 129, 152, 175, and 277)
subset(d_all, id_num != "129" & id_num != "152" & id_num != "175" & id_num != "277")
# great, we've removed our 4 participants completely from our dataframe d_all and now have all of the participants we can use for analyses

```

```{r explicit concepts and sums}
# so, from here, we'll use two factors and create average scores for them

# creating our new dataframe
d_explicitconcepts <- d_all %>% dplyr::select(contains(c("age", "gender", "control...6", "relig_attendserv", "relig_tradition", "explicit_concepts")))

# recoding gender here to use in our reg
d_explicitconcepts$gender <- dplyr::recode(d_explicitconcepts$gender, 'Male' = 1, 'Female'=2)
d_explicitconcepts$control...6 <- recode(d_explicitconcepts$control...6, 'Really Disagree' = 6, 'Disagree'=5, 'Kind of Disagree' = 4, 'Kind of Agree' = 3, 'Agree' = 2, 'Really Agree' = 1)
d_explicitconcepts$relig_attendserv <- recode(d_explicitconcepts$relig_attendserv, 'Never' = 1, 'Less than once a year'=2, 'A few times a year' = 3, 'A few times a month' = 4, 'A few times a week' = 5, 'Daily' = 6)
d_explicitconcepts$relig_tradition <- recode(d_explicitconcepts$relig_tradition, 'Not at all important' = 1, 'Minimally important'=2, 'Moderately important' = 3, 'Very important' = 4)

d_explicitconcepts$explicit_concepts <- recode(d_explicitconcepts$explicit_concepts, "Jordan, who says God doesn't really make things happen in people's lives." = "Jordan, who says God doesn't really make things happen in people's lives.", "Riley, who says God makes things happen in people's lives, but only at special times." = "Riley, who says God makes things happen in people's lives, but only at special times.", "Riley, who says God makes things happen in people's lives, but only special times." = "Riley, who says God makes things happen in people's lives, but only at special times.", "Sam, who says God makes things happen in people's lives, almost every day." = "Sam, who says God makes things happen in people's lives, almost every day.")

d_explicitconcepts$explicit_concepts <- recode_factor(d_explicitconcepts$explicit_concepts, "Jordan, who says God doesn't really make things happen in people's lives." = "Jordan", "Riley, who says God makes things happen in people's lives, but only at special times." = "Riley", "Riley, who says God makes things happen in people's lives, but only special times" = "Riley", "Sam, who says God makes things happen in people's lives, almost every day." = "Sam")

d_explicitconcepts$gender <- as.factor(d_explicitconcepts$gender)
d_explicitconcepts$control <- as.numeric(d_explicitconcepts$control...6)
d_explicitconcepts$relig_attendserv <- as.numeric(d_explicitconcepts$relig_attendserv)
d_explicitconcepts$relig_tradition <- as.numeric(d_explicitconcepts$relig_tradition)

#omitting NAs
d_explicitconcepts <- na.omit(d_explicitconcepts)

#deleting the old control...6 row
d_explicitconcepts <- d_explicitconcepts[,-3]  # Ian Fellows

# creating sum scores for our 2 factors (environment and people)
d_explicitconcepts$religiosity <- rowSums(d_explicitconcepts[, c(3, 4)]/2)
```

```{r explicit concepts regs}
# libraries for multinomial reg
library(foreign)
library(nnet)

levels(d_explicitconcepts$explicit_concepts)

# Setting the reference
d_explicitconcepts$explicit_concepts <- relevel(d_explicitconcepts$explicit_concepts, ref = "Jordan")

require(nnet)
# Training the multinomial model
multinom_model <- multinom(explicit_concepts ~ ., data = d_explicitconcepts)

# Checking the model
summary(multinom_model)

# Just like binary logistic regression, we need to convert the coefficients to odds by taking the exponential of the coefficients.
exp(coef(multinom_model))

# The predicted values are saved as fitted.values in the model object. Let’s see the top 6 observations.
head(round(fitted(multinom_model), 2))
# The multinomial regression predicts the probability of a particular observation to be part of the said level. This is what we are seeing in the above table. Columns represent the classification levels and rows represent the observations.

####################################
# HL got lost here 
####################################

```

```{r multinomial reg another way}
# Starting our example by import the data into R
library(haven)
d_explicit <- d_explicitconcepts # Get a new copy of data
summary(d_explicit)

library(jmv)

# Load the multinom package
library(nnet)
# Since we are going to use Academic as the reference group, we need relevel the group.
d_explicit$explicit_concepts2 <- relevel(as.factor(d_explicit$explicit_concepts), ref = "Jordan")
#d_explicit$ses <- as.factor(d_explicit$ses)
levels(d_explicit$explicit_concepts2)

OIM <- multinom(explicit_concepts2 ~ 1, data = d_explicit)
summary(OIM)

multi_mo <- multinom(explicit_concepts2 ~ religiosity + control + age, data = d_explicit,model=TRUE)
summary(multi_mo)

# Check the Z-score for the model (wald Z)
z <- summary(multi_mo)$coefficients/summary(multi_mo)$standard.errors
z

# 2-tailed z test
p <- (1 - pnorm(abs(z), 0, 1)) * 2
p

# Check the predicted probability for each program
head(multi_mo$fitted.values,30)

# We can get the predicted result by use predict function
head(predict(multi_mo),30)

# Test the goodness of fit
chisq.test(d_explicit$explicit_concepts2,predict(multi_mo))

# Use the lmtest package to run Likelihood Ratio Tests
library(lmtest)
lrtest(multi_mo, "religiosity") 
lrtest(multi_mo, "control") 
lrtest(multi_mo, "age") 

# Let's check our model again
summary(multi_mo)

# extract the coefficients from the model and exponentiate
exp(coef(multi_mo))
```

```{r multinomial predicted model}
# let's convert our data to tall format so we can include all of the same plots on the same figure
library(reshape2)
library(car)
d_explicit_reshaped <- melt(d_explicit, id.vars= c("age", "explicit_concepts2"))

library(effects)
plot(Effect("religiosity",multi_mo))

#shows predictions with confidence bands
relig <- plot(Effect("religiosity",multi_mo),multiline=T, xlab = "Religiosity", ylab= "Explicit concepts (probability)")

relig + plot(x, y, main="title", sub="subtitle",
  xlab="X-axis label", ylab="y-axix label",
  xlim=c(xmin, xmax), ylim=c(ymin, ymax))

plot(Effect("control",multi_mo),multiline=T)

#shows multiple lines of predictions in the same plot
plot(Effect("religiosity",multi_mo),style="stacked")
# shows a stacked vertical bar chart of predictions

```

```{r ggplot effects modeling}

```


