---
title: "Effects of age, religiosity, and control on interventionist concepts
 Analysis"
author: "Hannah Lunkenheimer"
date: "`r Sys.Date()`"
output: html_document
---
# Effects of age, religiosity, and control on interventionist concepts

HOW ARE WE MEASURING RELIGIOSITY????

## This R Markdown file includes the following, each separated into chunks:

1. Exploratory factor analysis to decide factor groupings in the intervention items
2. Histograms of each intervention item, split by gender
3. Linear regression models with age, control, gender for environment, people, and total intervention scores
4. Figures with predicted reg lines (by gender) for each environment, people, and total intervention scores

iii.	Effects of age, etc on “intervention frequency task” (Does God make..?). Would just sum number of yes responses as dv.
1.	Linear regression (+histogram of each question. Factor analysis to determine clusters)

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(moonBook)
library(dplyr)

# importing the data
d_all <- read_csv("data/Cielo1_MergedFull_practice.csv")

# now let's view our data
#View(d_all)

# some participant data needs to be thrown out completely according to the red rows in our CSV file, so let's remove those participants completely here (ID 129, 152, 175, and 277)
subset(d_all, id_num != "129" & id_num != "152" & id_num != "175" & id_num != "277")
# great, we've removed our 4 participants completely from our dataframe d_all and now have all of the participants we can use for analyses

```

## Interventionist factor analysis 

```{r age intervention task fa}
# here is some of my old code on doing factor analysis

# we're selecting our subset of data and calling it to a new dataframe
d_fa <- d_all %>% dplyr::select(starts_with("help_"), starts_with("helop_friends")) 

# if any recoding needs to be done to the whole dataframe, we use this code below: (idk why we need to name a new df, but we do)

d_fa1 <- d_fa %>% 
  mutate_at(vars(1:14),
   ~as.numeric(dplyr::recode(.,
    "Never"=1,
    "Only at special times"=2,
    "Pretty often"=3,
    "Always"=4,
    "always" = 4,
    "IDK" = 5)))

View(d_fa1)

d_fa1 <- na.omit(d_fa1)
View(d_fa1)

# Extract number of factors
ev <- eigen(cor(d_fa1)) # get eigenvalues
ap <- parallel(subject=nrow(d_fa1),var=ncol(d_fa1),              rep=100,cent=.05)
nS <- nScree(x=ev$values, aparallel=ap$eigen$qevpea)
plotnScree(nS)

## Exploratory Factor analysis, testing with 3 factors and 2 factors to start, using varimax rotation for all
fact3 <- factanal(d_fa1, 3, rotation="varimax") 
print(fact3, digits=2, cutoff=.3, sort=TRUE)

fact2 <- factanal(d_fa1, 2, rotation="varimax") 
print(fact2, digits=2, cutoff=.3, sort=TRUE)

# this is to see if 1 factor is fine, which we'd then do a principal components analysis if this was the best loading
#fact <- factanal(d_all, 1, rotation="varimax") # show improvement 5, 4, 3
#print(fact, digits=2, cutoff=.3, sort=TRUE)

# Reduce factors- we do this to see if taking out items makes the loadings more clear. regardless of the outcome we find, it's up to our discretion as researchers on whether or not to omit certain items from a set of questions based on rationale
# d_all <- d_all %>% select(- Epistemic_4) %>% select(- Epistemic_6) # Why? 
# fact <- factanal(d_all, 3, rotation="varimax")
# print(fact, digits=2, cutoff=.3, sort=TRUE) # Optimal model w/3 factors 

# here we're plotting our factors (3 and 2) to visually see where the items are loading
load <- fact3$loadings[,1:3]
plot(load,type="n") # set up plot
text(load,labels=names(d_fa1),cex=.7) # add variable names

load <- fact2$loadings[,1:2]
plot(load,type="n") # set up plot
text(load,labels=names(d_fa1),cex=.7) # add variable names

# i can see here that we have two distinct groups (i prefer 2 factors to 3) where the first factor loads seasons, sun, and plants (nature/environment) and the second factor loads god's intervening with people (not the environment)
```

```{r age intervention factor sums}
# so, from here, we'll use two factors and create average scores for them

# creating our new dataframe
d_intervention <- d_all %>% dplyr::select(starts_with("help_"), contains(c("helop_friends", "age", "gender", "control...6")))

# recoding intervention colomns 
d_intervention <- d_intervention %>% 
  mutate_at(vars(1:14),
   ~as.numeric(dplyr::recode(.,
    "Never"=1,
    "Only at special times"=2,
    "Pretty often"=3,
    "Always"=4,
    "always" = 4,
    "IDK" = 5)))

# recoding gender here to use in our reg
d_intervention$gender <- recode(d_intervention$gender, 'Male' = 1, 'Female'=2)
d_intervention$control...6 <- recode(d_intervention$control...6, 'Really Disagree' = 1, 'Disagree'=2, 'Kind of Disagree' = 3, 'Kind of Agree' = 4, 'Agree' = 5, 'Really Agree' = 6)

d_intervention$gender <- as.factor(d_intervention$gender)
d_intervention$control <- as.numeric(d_intervention$control...6)

#omitting NAs
d_intervention <- na.omit(d_intervention)

# creating sum scores for our 2 factors (environment and people)
d_intervention$environment <- rowSums(d_intervention[,c(2, 3, 4)]/3)
d_intervention$people <- rowSums(d_intervention[,c(1, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14)]/11)
d_intervention$totalinter <- rowSums(d_intervention[, c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14)]/14)

```

## Histograms of each interventionist item

```{r intervention histograms}

i_sick_plot <- ggplot(d_intervention, aes(help_sick, fill=gender)) +
  geom_bar() +
  labs(x='Child response', y="Participants", title ="Does God help sick people get better?") +
  theme_light() +
  scale_x_discrete(limits = c("1", "2", "3", 
                             "4"),
                   labels = c("Never", "Only at special times", 
                              "Pretty often", "Always")) +
  scale_fill_discrete(labels=c('Male', 'Female'))

i_sun_plot <- ggplot(d_intervention, aes(help_sun, fill=gender)) +
  geom_bar() +
  labs(x='Child response', y="Participants", title ="Does God help the sun come up?") +
  theme_light() +
  scale_x_discrete(limits = c("1", "2", "3", 
                             "4"),
                   labels = c("Never", "Only at special times", 
                              "Pretty often", "Always")) +
  scale_fill_discrete(labels=c('Male', 'Female'))

i_season_plot <- ggplot(d_intervention, aes(help_seasons, fill=gender)) +
  geom_bar() +
  labs(x='Child response', y="Participants", title ="Does God help make the seasons change?") +
  theme_light() +
  scale_x_discrete(limits = c("1", "2", "3", 
                             "4"),
                   labels = c("Never", "Only at special times", 
                              "Pretty often", "Always")) +
  scale_fill_discrete(labels=c('Male', 'Female'))

i_plants_plot <- ggplot(d_intervention, aes(help_plants, fill=gender)) +
  geom_bar() +
  labs(x='Child response', y="Participants", title ="Does God help plants grow?") +
  theme_light() +
  scale_x_discrete(limits = c("1", "2", "3", 
                             "4"),
                   labels = c("Never", "Only at special times", 
                              "Pretty often", "Always")) +
  scale_fill_discrete(labels=c('Male', 'Female'))

i_love_plot <- ggplot(d_intervention, aes(help_love, fill=gender)) +
  geom_bar() +
  labs(x='Child response', y="Participants", title ="Does God help people fall in love?") +
  theme_light() +
  scale_x_discrete(limits = c("1", "2", "3", 
                             "4"),
                   labels = c("Never", "Only at special times", 
                              "Pretty often", "Always")) +
  scale_fill_discrete(labels=c('Male', 'Female'))

i_friends_plot <- ggplot(d_intervention, aes(helop_friends, fill=gender)) +
  geom_bar() +
  labs(x='Child response', y="Participants", title ="Does God help people become friends?") +
  theme_light() +
  scale_x_discrete(limits = c("1", "2", "3", 
                             "4"),
                   labels = c("Never", "Only at special times", 
                              "Pretty often", "Always")) +
  scale_fill_discrete(labels=c('Male', 'Female'))

i_dreams_plot <- ggplot(d_intervention, aes(help_dreams, fill=gender)) +
  geom_bar() +
  labs(x='Child response', y="Participants", title ="Does God help give people good dreams?") +
  theme_light() +
  scale_x_discrete(limits = c("1", "2", "3", 
                             "4"),
                   labels = c("Never", "Only at special times", 
                              "Pretty often", "Always")) +
  scale_fill_discrete(labels=c('Male', 'Female'))

i_find_plot <- ggplot(d_intervention, aes(help_find, fill=gender)) +
  geom_bar() +
  labs(x='Child response', y="Participants", title ="Does God help find lost things?") +
  theme_light() +
  scale_x_discrete(limits = c("1", "2", "3", 
                             "4"),
                   labels = c("Never", "Only at special times", 
                              "Pretty often", "Always")) +
  scale_fill_discrete(labels=c('Male', 'Female'))

i_decide_plot <- ggplot(d_intervention, aes(help_decide, fill=gender)) +
  geom_bar() +
  labs(x='Child response', y="Participants", title ="Does God help people make hard decisions?") +
  theme_light() +
  scale_x_discrete(limits = c("1", "2", "3", 
                             "4"),
                   labels = c("Never", "Only at special times", 
                              "Pretty often", "Always")) +
  scale_fill_discrete(labels=c('Male', 'Female'))

i_job_plot <- ggplot(d_intervention, aes(help_job, fill=gender)) +
  geom_bar() +
  labs(x='Child response', y="Participants", title ="Does God ever help people do well in school or at their job?") +
  theme_light() +
  scale_x_discrete(limits = c("1", "2", "3", 
                             "4"),
                   labels = c("Never", "Only at special times", 
                              "Pretty often", "Always")) +
  scale_fill_discrete(labels=c('Male', 'Female'))

i_sports_plot <- ggplot(d_intervention, aes(help_sports, fill=gender)) +
  geom_bar() +
  labs(x='Child response', y="Participants", title ="Does God help people do well in games and sports?") +
  theme_light() +
  scale_x_discrete(limits = c("1", "2", "3", 
                             "4"),
                   labels = c("Never", "Only at special times", 
                              "Pretty often", "Always")) +
  scale_fill_discrete(labels=c('Male', 'Female'))

i_happy_plot <- ggplot(d_intervention, aes(help_happy, fill=gender)) +
  geom_bar() +
  labs(x='Child response', y="Participants", title ="Does God help people feel happier?") +
  theme_light() +
  scale_x_discrete(limits = c("1", "2", "3", 
                             "4"),
                   labels = c("Never", "Only at special times", 
                              "Pretty often", "Always")) +
  scale_fill_discrete(labels=c('Male', 'Female'))

i_brave_plot <- ggplot(d_intervention, aes(help_brave, fill=gender)) +
  geom_bar() +
  labs(x='Child response', y="Participants", title ="Does God help people feel braver about scary things?") +
  theme_light() +
  scale_x_discrete(limits = c("1", "2", "3", 
                             "4"),
                   labels = c("Never", "Only at special times", 
                              "Pretty often", "Always")) +
  scale_fill_discrete(labels=c('Male', 'Female'))

i_safe_plot <- ggplot(d_intervention, aes(help_safe, fill=gender)) +
  geom_bar() +
  labs(x='Child response', y="Participants", title ="Does God keep people safe from danger?") +
  theme_light() +
  scale_x_discrete(limits = c("1", "2", "3", 
                             "4"),
                   labels = c("Never", "Only at special times", 
                              "Pretty often", "Always")) +
  scale_fill_discrete(labels=c('Male', 'Female'))

i_sun_plot
i_season_plot
i_plants_plot

i_sick_plot
i_love_plot
i_friends_plot
i_dreams_plot
i_find_plot
i_decide_plot
i_job_plot
i_sports_plot
i_happy_plot
i_brave_plot
i_safe_plot
```

```{r interventions altogether x gender bar figure}

d_intervention2 <- d_all %>% dplyr::select(starts_with("help_"), contains(c("helop_friends", "age", "gender")))

# recoding intervention colomns 
d_intervention2 <- d_intervention2 %>% 
  mutate_at(vars(1:14),
   ~as.numeric(dplyr::recode(.,
    "Never"=1,
    "Only at special times"=2,
    "Pretty often"=3,
    "Always"=4,
    "always" = 4,
    "IDK" = 5)))

# recoding gender here to use in our reg
d_intervention2$gender <- recode(d_intervention2$gender, 'Male' = 1, 'Female'=2)

d_intervention2$gender <- as.factor(d_intervention2$gender)

#omitting NAs
d_intervention2 <- na.omit(d_intervention2)

# let's convert our data to tall format so we can include all of the same plots on the same figure
library(reshape2)
d_intervention_reshaped <- melt(d_intervention2, id.vars= c("age", "gender"))

d_intervention_reshaped$value <- as.factor(d_intervention_reshaped$value)

#let's view our tall data now
View(d_intervention_reshaped)

# here, i'm making a dataframe with frequency counts added in
# d_intervention_reshaped_counts <- table(d_intervention_reshaped$value, d_intervention_reshaped$variable, d_intervention_reshaped$gender)
# addmargins(d_intervention_reshaped_counts)
# round(prop.table(d_intervention_reshaped_counts,2)*100,digits=0)
# df_irc <- as.data.frame(d_intervention_reshaped_counts)
# View(df_irc)
# creating our ggplot for all exist questions including both genders together. i'm labeling it p_exist because we're making a plot for the exist questions
p_irc <- ggplot(data = d_intervention_reshaped, aes(x = variable, y = age, fill = value)) +
       geom_bar(stat = "identity", width = .5) +
      theme_classic() +
      labs(title="Children's responses to interventionist questions", x ="Item", y = "Counts", fill = "Response") +
      theme(axis.text.x = element_text(angle=90))

# fixing the x axis labels
p_irc <- p_irc + scale_fill_discrete(labels=c("1" = "Never", "2" = "Only on special occasions", "3" = "Pretty often", "4" = "Always", "5" = "I don't know"))

# faceting by gender
# p_irc <- p_irc + facet_wrap(~Var3, ncol = 1) +
#     theme(panel.spacing = unit(1, "lines"))

p_irc

```

##Environment interventionist concepts only

```{r environment intervention regs}
library(arm)

# we start by creating our null model with a fixed slope and no predictors
null_model <- lm(environment ~ 1, data = d_intervention)
summary(null_model)
tab_model(null_model)
coef(null_model)

reg1 <- lm(environment ~ age, data = d_intervention)
summary(reg1)
tab_model(null_model, reg1)

reg2 <- lm(environment ~ age + gender, data = d_intervention)
summary(reg2)
tab_model(null_model, reg1, reg2)

reg3 <- lm(environment ~ age + gender + control, data = d_intervention)
summary(reg3)
tab_model(null_model, reg1, reg2, reg3)

reg4 <- lm(environment ~ age + gender + control + age*gender + age*control + gender*control, data = d_intervention)
summary(reg4)
tab_model(null_model, reg1, reg2, reg3, reg4)

anova(null_model, reg1, reg2)

AIC(reg1, reg2, reg3)
```

```{r environment intervention plot}
# how should we visualize this data?

g_environment <- ggplot(d_intervention,aes(y=environment,x=age)) +
  geom_point() +
  geom_jitter() +
  geom_smooth(method="lm") +
  theme_minimal()

# plotting our data without reg lines
g_environment

# You can make interactive plot easily with ggPredict() function included in ggiraphExtra package. this is me just messing around.
library(ggiraphExtra)
require(ggiraph)
require(ggiraphExtra)
require(plyr)
ggPredict(reg1,se=TRUE,interactive=TRUE)

reg1 <- lm(environment ~ age, data = d_intervention)
summary(reg1)
tab_model(null_model, reg1)

g_environment1 <- ggplot(data=d_intervention, aes(x=age, y=environment)) +
  geom_bar(stat="identity", fill="purple")+
  theme_minimal()

g_environment1

# need to add error bars to this figure

reg2 <- lm(environment ~ age + gender, data = d_intervention)
summary(reg2)
tab_model(null_model, reg1, reg2)

#making the figure with reg2
equation1=function(x){coef(reg2)[2]*x+coef(reg2)[1]}
equation2=function(x){coef(reg2)[2]*x+coef(reg2)[1]+coef(reg2)[3]}

g_environment2 <- ggplot(d_intervention,aes(y=environment,x=age,color=gender)) + 
        geom_point() +
        stat_function(fun=equation1,geom="line",color=scales::hue_pal()(2)[1]) +
        stat_function(fun=equation2,geom="line",color=scales::hue_pal()(2)[2]) +
        theme_minimal()

g_environment2 <- g_environment2 + geom_jitter(aes(color = gender), width = 0.2, height = 0.2)

g_environment2 + labs(x = 'Age', y = 'God intervention score - Environment') + 
  scale_color_discrete(labels=c('Male', 'Female'))

#making the figure with reg3
equation1.1=function(x){coef(reg3)[2]*x+coef(reg3)[1]}
equation2.1=function(x){coef(reg3)[2]*x+coef(reg3)[1]+coef(reg3)[3]}

g_environment2.1 <- ggplot(d_intervention,aes(y=environment,x=age,color=gender)) + 
        geom_point() +
        stat_function(fun=equation1.1,geom="line",color=scales::hue_pal()(2)[1]) +
        stat_function(fun=equation2.1,geom="line",color=scales::hue_pal()(2)[2]) +
        theme_minimal()

g_environment2.1 <- g_environment2.1 + geom_jitter(aes(color = gender), width = 0.2, height = 0.2)

g_environment2.1 + labs(x = 'Age', y = 'God intervention score - Environment') + 
  scale_color_discrete(labels=c('Male', 'Female'))


```

## People intervention concepts only

```{r people intervention regs}
# we start by creating our null model with a fixed slope and no predictors
null_modelp <- lm(people ~ 1, data = d_intervention)
summary(null_modelp)
tab_model(null_modelp)
coef(null_modelp)

reg1p <- lm(people ~ age, data = d_intervention)
summary(reg1p)
tab_model(null_modelp, reg1p)

reg2p <- lm(people ~ age + gender, data = d_intervention)
summary(reg2p)
tab_model(null_modelp, reg1p, reg2p)

anova(null_modelp, reg1p, reg2p)

AIC(reg1p, reg2p)

# we can see here that our second model is better (reg2)

```

```{r people intervention plot}
# how should we visualize this data?

g_people <- ggplot(d_intervention,aes(y=people,x=age)) +
  geom_point() +
  geom_jitter() +
  geom_smooth(method="lm") +
  theme_minimal()

# plotting our data without reg lines
g_people

# You can make interactive plot easily with ggPredict() function included in ggiraphExtra package. this is me just messing around.
library(ggiraphExtra)
require(ggiraph)
require(ggiraphExtra)
require(plyr)
ggPredict(reg1p,se=TRUE,interactive=TRUE)

reg1p <- lm(people ~ age, data = d_intervention)
summary(reg1p)
tab_model(null_modelp, reg1p)

# creating a bar plot with our data, need to add error bars to this figure

g_people1 <- ggplot(data=d_intervention, aes(x=age, y=people)) +
  geom_bar(stat="identity", fill="purple")+
  theme_minimal()

g_people1

# not sure what this function does- need to check
equation1p=function(x){coef(reg2p)[2]*x+coef(reg2p)[1]}
equation2p=function(x){coef(reg2p)[2]*x+coef(reg2p)[1]+coef(reg2p)[3]}

g_people2 <- ggplot(d_intervention,aes(y=people,x=age,color=gender)) + 
        geom_point() +
        stat_function(fun=equation1p,geom="line",color=scales::hue_pal()(2)[1]) +
        stat_function(fun=equation2p,geom="line",color=scales::hue_pal()(2)[2]) +
        theme_minimal()

g_people2.1 <- g_people2 + geom_jitter(aes(color = gender), width = 0.5, height = 0.5)

g_people2.2 <-g_people2.1 + labs(x = 'Age', y = 'God intervention score - People')

g_people2.3 <- g_people2.2 + scale_color_discrete(labels=c('Male', 'Female'))

g_people2.3
```

## Total intervention concepts all together

```{r total intervention regs}
# we start by creating our null model with a fixed slope and no predictors
null_modelt <- lm(totalinter ~ 1, data = d_intervention)
summary(null_modelt)
tab_model(null_modelt)
coef(null_modelt)

reg1t <- lm(totalinter ~ age, data = d_intervention)
summary(reg1t)
tab_model(null_modelt, reg1t)

reg2t <- lm(totalinter ~ age + gender, data = d_intervention)
summary(reg2t)
tab_model(null_modelt, reg1t, reg2t)

anova(null_modelt, reg1t, reg2t)

AIC(reg1t, reg2t)

# we can see here that our second model is better (reg2)

```

```{r total intervention plot}

g_total <- ggplot(d_intervention,aes(y=totalinter,x=age)) +
  geom_point() +
  geom_jitter() +
  geom_smooth(method="lm") +
  theme_minimal()

# plotting our data without reg lines
g_total

# running reg with just age
reg1t <- lm(people ~ age, data = d_intervention)
summary(reg1t)
tab_model(null_modelt, reg1t)

# creating a bar plot with our data, need to add error bars to this figure

g_total1 <- ggplot(data=d_intervention, aes(x=age, y=totalinter)) +
  geom_bar(stat="identity", fill="purple")+
  theme_minimal()

g_total1

# not sure what this function does- need to check
equation1t=function(x){coef(reg2t)[2]*x+coef(reg2t)[1]}
equation2t=function(x){coef(reg2t)[2]*x+coef(reg2t)[1]+coef(reg2t)[3]}

g_total2 <- ggplot(d_intervention,aes(y=totalinter,x=age,color=gender)) + 
        geom_point() +
        stat_function(fun=equation1t,geom="line",color=scales::hue_pal()(2)[1]) +
        stat_function(fun=equation2t,geom="line",color=scales::hue_pal()(2)[2]) +
        theme_minimal()

g_total2.1 <- g_total2 + geom_jitter(aes(color = gender), width = 0.5, height = 0.5)

g_total2.2 <-g_total2.1 + labs(x = 'Age', y = 'God intervention score - Total')

g_total2.3 <- g_total2.2 + scale_color_discrete(labels=c('Male', 'Female'))

g_total2.3
```