---
title: "Effects of age, religiosity, and control on interventionist concepts
 Analysis"
author: "Hannah Lunkenheimer"
date: "`r Sys.Date()`"
output: html_document
---
# Effects of age, religiosity, and control on interventionist concepts

## This R Markdown file includes the following, each separated into chunks:

1. Exploratory factor analysis to decide factor groupings in the intervention items
2. Histograms of each intervention item, split by gender
3. Linear regression models with age, control, gender for environment, people, and total intervention scores
4. Figures with predicted reg lines (by gender) for each environment, people, and total intervention scores

iii.	Effects of age, etc on “intervention frequency task” (Does God make..?). Would just sum number of yes responses as dv.
1.	Linear regression (+histogram of each question. Factor analysis to determine clusters)

```{r setup, include=FALSE}

knitr::opts_chunk$set(dev = "png",
                      dpi = 300,
                      echo = FALSE,
                      cache = TRUE)

library(moonBook)
library(dplyr)
library(readr)
library(ggplot2)
library(sjPlot)
library(reshape2)

# importing the data
d_all <- read_csv("data/Cielo1_MergedFull_practice.csv")

# now let's view our data
#View(d_all)

# some participant data needs to be thrown out completely according to the red rows in our CSV file, so let's remove those participants completely here (ID 129, 152, 175, and 277)
subset(d_all, id_num != "129" & id_num != "152" & id_num != "175" & id_num != "277")
# great, we've removed our 4 participants completely from our dataframe d_all and now have all of the participants we can use for analyses

```

## Interventionist factor analysis 

```{r age intervention task fa}
# here is some of my old code on doing factor analysis

# we're selecting our subset of data and calling it to a new dataframe
d_fa <- d_all %>% dplyr::select(starts_with("help_"), starts_with("helop_friends")) 
# if any recoding needs to be done to the whole dataframe, we use this code below: (idk why we need to name a new df, but we do)

d_fa1 <- d_fa %>% 
  mutate_at(vars(1:14),
   ~as.numeric(dplyr::recode(.,
    "Never"=1,
    "Only at special times"=2,
    "Pretty often"=3,
    "Always"=4,
    "always" = 4,
    "IDK" = 5)))


d_fa1 <- na.omit(d_fa1)

d_fa1 <- d_fa1 %>% 
       rename("help_friends" = "helop_friends")
# Extract number of factors
ev <- eigen(cor(d_fa1)) # get eigenvalues
#ap <- parallel(subject=nrow(d_fa1),var=ncol(d_fa1),              rep=100,cent=.05)
#nS <- nScree(x=ev$values, aparallel=ap$eigen$qevpea)
#plotnScree(nS)

## Exploratory Factor analysis, testing with 3 factors and 2 factors to start, using varimax rotation for all
fact5 <- factanal(d_fa1, 5, rotation="varimax") 
print(fact5, digits=2, cutoff=.3, sort=TRUE)

fact4 <- factanal(d_fa1, 4, rotation="varimax") 
print(fact4, digits=2, cutoff=.3, sort=TRUE)

fact3 <- factanal(d_fa1, 3, rotation="varimax") 
print(fact3, digits=2, cutoff=.3, sort=TRUE)

fact2 <- factanal(d_fa1, 2, rotation="varimax") 
print(fact2, digits=2, cutoff=.3, sort=TRUE)


tab_fa(d_fa1, nmbr.fctr = 5, rotation = "varimax", title = "Factor Analysis",)
tab_fa(d_fa1, nmbr.fctr = 4, rotation = "varimax", title = "Factor Analysis",)
tab_fa(d_fa1, nmbr.fctr = 2, rotation = "varimax", title = "Factor Analysis",)

library(psych)
KMO(d_fa1)

library(stats)

# Conduct Bartlett's test of sphericity
bartlett_result <- cortest.bartlett(d_fa1)

# Print the result
bartlett_result$p.value
# this is to see if 1 factor is fine, which we'd then do a principal components analysis if this was the best loading
#fact <- factanal(d_all, 1, rotation="varimax") # show improvement 5, 4, 3
#print(fact, digits=2, cutoff=.3, sort=TRUE)

# Reduce factors- we do this to see if taking out items makes the loadings more clear. regardless of the outcome we find, it's up to our discretion as researchers on whether or not to omit certain items from a set of questions based on rationale
# d_all <- d_all %>% select(- Epistemic_4) %>% select(- Epistemic_6) # Why? 
# fact <- factanal(d_all, 3, rotation="varimax")
# print(fact, digits=2, cutoff=.3, sort=TRUE) # Optimal model w/3 factors 

# here we're plotting our factors (3 and 2) to visually see where the items are loading
load4 <- fact4$loadings[,1:4]
plot(load4,type="n") # set up plot
text(load4,labels=names(d_fa1),cex=.7) # add variable names

load3 <- fact3$loadings[,1:3]
plot(load3,type="n") # set up plot
text(load3,labels=names(d_fa1),cex=.7) # add variable names

load5 <- fact5$loadings[,1:5]
plot(load5,type="n") # set up plot
text(load5,labels=names(d_fa1),cex=.7) # add variable names

# i can see here that we have two distinct groups (i prefer 2 factors to 3) where the first factor loads seasons, sun, and plants (nature/environment) and the second factor loads god's intervening with people (not the environment)
```

```{r age intervention factor sums}
# so, from here, we'll use two factors and create average scores for them

# creating our new dataframe
d_intervention <- d_all %>% dplyr::select(starts_with("help_"), contains(c("helop_friends", "age", "gender", "control...6", "relig_attendserv", "relig_tradition", "id_num")))

# recoding intervention colomns 
d_intervention <- d_intervention %>% 
  mutate_at(vars(1:14),
   ~as.numeric(dplyr::recode(.,
    "Never"=1,
    "Only at special times"=2,
    "Pretty often"=3,
    "Always"=4,
    "always" = 4,
    "IDK" = 5)))

# recoding gender here to use in our reg
d_intervention$gender <- dplyr::recode(d_intervention$gender, 'Male' = 1, 'Female'=2)
d_intervention$control...6 <- dplyr::recode(d_intervention$control...6, 'Really Disagree' = 6, 'Disagree'=5, 'Kind of Disagree' = 4, 'Kind of Agree' = 3, 'Agree' = 2, 'Really Agree' = 1)
d_intervention$relig_attendserv <- dplyr::recode(d_intervention$relig_attendserv, 'Never' = 1, 'Less than once a year'=2, 'A few times a year' = 3, 'A few times a month' = 4, 'A few times a week' = 5, 'Daily' = 6)
d_intervention$relig_tradition <- dplyr::recode(d_intervention$relig_tradition, 'Not at all important' = 1, 'Minimally important'=2, 'Moderately important' = 3, 'Very important' = 4)

d_intervention$help_friends <- d_intervention$helop_friends


d_intervention$gender <- as.factor(d_intervention$gender)
d_intervention$control <- as.numeric(d_intervention$control...6)
d_intervention$relig_attendserv <- as.numeric(d_intervention$relig_attendserv)
d_intervention$relig_tradition <- as.numeric(d_intervention$relig_tradition)

#omitting NAs
d_intervention <- na.omit(d_intervention)

# creating sum scores for our 2 factors (environment and people)
d_intervention$environment <- rowSums(d_intervention[,c(2, 3, 4)]/3) #plants, sun, seasons
d_intervention$psych <- rowSums(d_intervention[,c(6, 8, 11, 12)]/4) #dreams, happy, brave decisions
d_intervention$health <- rowSums(d_intervention[,c(1, 13)]/2) #sick, safe
d_intervention$outcome <- rowSums(d_intervention[,c(7, 9, 10)]/3) #job, sports, find
d_intervention$social <- rowSums(d_intervention[,c(5, 14)]/2) #love, friends

d_intervention$people <- rowSums(d_intervention[,c(1, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14)]/11)
d_intervention$totalinter <- rowSums(d_intervention[, c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14)]/14)
d_intervention$religiosity <- rowSums(d_intervention[, c(18, 19)]/2)

#creating a filter to exclude IDK responses from analyses
d_intervention2 <- dplyr::filter(d_intervention, help_plants != 5 | help_love != 5) 
d_intervention2 <- dplyr::filter(d_intervention2, help_love != 5) 


```

## Histograms of each interventionist item

```{r intervention histograms}
i_sick_plot <- ggplot(d_intervention2, aes(help_sick, fill=gender)) +
  geom_bar() +
  labs(x='Child response', y="Participants", title ="Does God help sick people get better?") +
  theme_light() +
  scale_x_discrete(limits = c("1", "2", "3", 
                             "4"),
                   labels = c("Never", "Only at special times", 
                              "Pretty often", "Always")) +
  scale_fill_discrete(labels=c('Male', 'Female'))

i_sun_plot <- ggplot(d_intervention2, aes(help_sun, fill=gender)) +
  geom_bar() +
  labs(x='Child response', y="Participants", title ="Does God help the sun come up?") +
  theme_light() +
  scale_x_discrete(limits = c("1", "2", "3", 
                             "4"),
                   labels = c("Never", "Only at special times", 
                              "Pretty often", "Always")) +
  scale_fill_discrete(labels=c('Male', 'Female'))

i_season_plot <- ggplot(d_intervention2, aes(help_seasons, fill=gender)) +
  geom_bar() +
  labs(x='Child response', y="Participants", title ="Does God help make the seasons change?") +
  theme_light() +
  scale_x_discrete(limits = c("1", "2", "3", 
                             "4"),
                   labels = c("Never", "Only at special times", 
                              "Pretty often", "Always")) +
  scale_fill_discrete(labels=c('Male', 'Female'))

i_plants_plot <- ggplot(d_intervention2, aes(help_plants, fill=gender)) +
  geom_bar() +
  labs(x='Child response', y="Participants", title ="Does God help plants grow?") +
  theme_light() +
  scale_x_discrete(limits = c("1", "2", "3", 
                             "4"),
                   labels = c("Never", "Only at special times", 
                              "Pretty often", "Always")) +
  scale_fill_discrete(labels=c('Male', 'Female'))

i_love_plot <- ggplot(d_intervention2, aes(help_love, fill=gender)) +
  geom_bar() +
  labs(x='Child response', y="Participants", title ="Does God help people fall in love?") +
  theme_light() +
  scale_x_discrete(limits = c("1", "2", "3", 
                             "4"),
                   labels = c("Never", "Only at special times", 
                              "Pretty often", "Always")) +
  scale_fill_discrete(labels=c('Male', 'Female'))

i_friends_plot <- ggplot(d_intervention2, aes(helop_friends, fill=gender)) +
  geom_bar() +
  labs(x='Child response', y="Participants", title ="Does God help people become friends?") +
  theme_light() +
  scale_x_discrete(limits = c("1", "2", "3", 
                             "4"),
                   labels = c("Never", "Only at special times", 
                              "Pretty often", "Always")) +
  scale_fill_discrete(labels=c('Male', 'Female'))

i_dreams_plot <- ggplot(d_intervention2, aes(help_dreams, fill=gender)) +
  geom_bar() +
  labs(x='Child response', y="Participants", title ="Does God help give people good dreams?") +
  theme_light() +
  scale_x_discrete(limits = c("1", "2", "3", 
                             "4"),
                   labels = c("Never", "Only at special times", 
                              "Pretty often", "Always")) +
  scale_fill_discrete(labels=c('Male', 'Female'))

i_find_plot <- ggplot(d_intervention2, aes(help_find, fill=gender)) +
  geom_bar() +
  labs(x='Child response', y="Participants", title ="Does God help find lost things?") +
  theme_light() +
  scale_x_discrete(limits = c("1", "2", "3", 
                             "4"),
                   labels = c("Never", "Only at special times", 
                              "Pretty often", "Always")) +
  scale_fill_discrete(labels=c('Male', 'Female'))

i_decide_plot <- ggplot(d_intervention2, aes(help_decide, fill=gender)) +
  geom_bar() +
  labs(x='Child response', y="Participants", title ="Does God help people make hard decisions?") +
  theme_light() +
  scale_x_discrete(limits = c("1", "2", "3", 
                             "4"),
                   labels = c("Never", "Only at special times", 
                              "Pretty often", "Always")) +
  scale_fill_discrete(labels=c('Male', 'Female'))

i_job_plot <- ggplot(d_intervention2, aes(help_job, fill=gender)) +
  geom_bar() +
  labs(x='Child response', y="Participants", title ="Does God ever help people do well in school or at their job?") +
  theme_light() +
  scale_x_discrete(limits = c("1", "2", "3", 
                             "4"),
                   labels = c("Never", "Only at special times", 
                              "Pretty often", "Always")) +
  scale_fill_discrete(labels=c('Male', 'Female'))

i_sports_plot <- ggplot(d_intervention2, aes(help_sports, fill=gender)) +
  geom_bar() +
  labs(x='Child response', y="Participants", title ="Does God help people do well in games and sports?") +
  theme_light() +
  scale_x_discrete(limits = c("1", "2", "3", 
                             "4"),
                   labels = c("Never", "Only at special times", 
                              "Pretty often", "Always")) +
  scale_fill_discrete(labels=c('Male', 'Female'))

i_happy_plot <- ggplot(d_intervention2, aes(help_happy, fill=gender)) +
  geom_bar() +
  labs(x='Child response', y="Participants", title ="Does God help people feel happier?") +
  theme_light() +
  scale_x_discrete(limits = c("1", "2", "3", 
                             "4"),
                   labels = c("Never", "Only at special times", 
                              "Pretty often", "Always")) +
  scale_fill_discrete(labels=c('Male', 'Female'))

i_brave_plot <- ggplot(d_intervention2, aes(help_brave, fill=gender)) +
  geom_bar() +
  labs(x='Child response', y="Participants", title ="Does God help people feel braver about scary things?") +
  theme_light() +
  scale_x_discrete(limits = c("1", "2", "3", 
                             "4"),
                   labels = c("Never", "Only at special times", 
                              "Pretty often", "Always")) +
  scale_fill_discrete(labels=c('Male', 'Female'))

i_safe_plot <- ggplot(d_intervention2, aes(help_safe, fill=gender)) +
  geom_bar() +
  labs(x='Child response', y="Participants", title ="Does God keep people safe from danger?") +
  theme_light() +
  scale_x_discrete(limits = c("1", "2", "3", 
                             "4"),
                   labels = c("Never", "Only at special times", 
                              "Pretty often", "Always")) +
  scale_fill_discrete(labels=c('Male', 'Female'))

i_sun_plot
i_season_plot
i_plants_plot

i_sick_plot
i_love_plot
i_friends_plot
i_dreams_plot
i_find_plot
i_decide_plot
i_job_plot
i_sports_plot
i_happy_plot
i_brave_plot
i_safe_plot
```


```{r intervention score x gender bar figure}

# here, i'm making a dataframe with frequency counts added in
d_intervention_reshaped_counts <- table(d_intervention_reshaped$value, d_intervention_reshaped$variable, d_intervention_reshaped$gender)
addmargins(d_intervention_reshaped_counts)
round(prop.table(d_intervention_reshaped_counts,2)*100,digits=0)
df_irc <- as.data.frame(d_intervention_reshaped_counts)

cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442")
#Turn your 'treatment' column into a character vector
df_irc$Var2 <- as.character(df_irc$Var2)
#Then turn it back into a factor with the levels in the correct order
df_irc$Var2 <- factor(df_irc$Var2, levels=c("help_sun", "help_seasons", "help_plants", "help_brave", "help_happy","help_sick", "help_safe", "helop_friends", "help_dreams", "help_love",  "help_decide",  "help_find", "help_job", "help_sports"))

# creating our ggplot for all exist questions including both genders together. i'm labeling it p_exist because we're making a plot for the exist questions
g_irc <- ggplot(data = df_irc, aes(x = Var2, y = Freq, fill = Var1)) +
    scale_fill_brewer(palette= "Paired", labels=c("1" = "Never", "2" = "Only on special occasions", "3" = "Pretty often", "4" = "Always", "5" = "I don't know")) +
       geom_bar(stat = "identity", width = .5) +
      theme_classic() +
      labs(title="Children's responses to intervention frequency questions", x = "Question", y = "Counts", fill = "Response") +
      theme(axis.text.x = element_text(angle=01))

#g_irc <- g_irc + scale_fill_discrete(labels=c("1" = "Never", "2" = "Only on special occasions", "3" = "Pretty #often", "4" = "Always", "5" = "I don't know"))


# changing the label names
g_irc <- g_irc + scale_x_discrete(labels=c("help_sick" = "Sick\npeople", "help_sun" = "Sun\nrise", "help_seasons" = "Seasons\nchange", "help_plants" = "Plants\ngrow", "help_love" = "Fall\nin\nlove", "help_dreams" = "Good\ndreams", "help_find" = "Find\nthings", "help_decide" = "Hard\ndecisions", "help_job" = "Good\nat\njob", "help_sports" = "Good\nat\nsports", "help_happy" = "Feel\nhappy", "help_brave" = "Feel\nbrave", "help_safe" = "Safe\nfrom\ndanger", "helop_friends"= "Become\nfriends"))

g_irc <- g_irc + theme(legend.position="bottom")

g_irc

```

##Environment interventionist concepts only

```{r environment intervention regs}
library(arm)

# we start by creating our null model with a fixed slope and no predictors
null_model <- lm(environment ~ 1, data = d_intervention2)
summary(null_model)
tab_model(null_model)
coef(null_model)

reg1 <- lm(environment ~ age, data = d_intervention2)
summary(reg1)
tab_model(null_model, reg1)

reg2 <- lm(environment ~ age + gender, data = d_intervention2)
summary(reg2)
tab_model(null_model, reg1, reg2)

reg3 <- lm(environment ~ age + gender + control, data = d_intervention2)
summary(reg3)
tab_model(null_model, reg1, reg2, reg3)

reg4 <- lm(environment ~ age + gender + control + religiosity + age*gender + age*control + gender*control + age*religiosity + gender*religiosity + control*religiosity, data = d_intervention2)
summary(reg4)
tab_model(null_model, reg1, reg2, reg3, reg4)

reg5 <- lm(environment ~ age + gender + control + religiosity  + gender*control, data = d_intervention2)
AIC(reg1, reg2, reg3, reg4, reg5)
anova(reg1, reg2, reg3, reg4, reg5)

```

```{r environment intervention regs part2}
reg4 <- lm(environment ~ age + gender + control + religiosity + age*gender + age*control + gender*control + age*religiosity + gender*religiosity + control*religiosity, data = d_intervention2)
summary(reg4)
reg5 <- lm(environment ~ age + gender + control + religiosity + gender*control, data = d_intervention2)
summary(reg5)
tab_model(reg1, reg4, reg5)
tab_model(reg5)
AIC(reg1, reg4, reg5)

#reg5 is the best model with age, gender, control, religiosity, and gender*control

```

```{r environment intervention plot}
# how should we visualize this data?
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442")

g_environment <- ggplot(d_intervention2,aes(y=environment,x=age)) +
  geom_point(color = "#999999") +
  geom_jitter() +
  geom_smooth(method="lm", color = "#E69F00") +
  theme_minimal()

# plotting our data without reg lines
g_environment


```

## People intervention concepts only

```{r people intervention regs}
# we start by creating our null model with a fixed slope and no predictors
null_modelp <- lm(people ~ 1, data = d_intervention)
summary(null_modelp)
tab_model(null_modelp)
coef(null_modelp)

reg1p <- lm(people ~ age, data = d_intervention)
summary(reg1p)
tab_model(null_modelp, reg1p)

reg2p <- lm(people ~ age + gender, data = d_intervention)
summary(reg2p)
tab_model(null_modelp, reg1p, reg2p)

reg3p <- lm(people ~ age + gender + control + religiosity + age*gender + age*control + gender*control + age*religiosity + gender*religiosity + control*religiosity, data = d_intervention)

reg4p <- lm(people ~ age + gender + control + religiosity + age*control + gender*control, data = d_intervention)

anova(null_modelp, reg1p, reg2p, reg3p, reg4p)
AIC(reg1p, reg2p, reg3p, reg4p)

anova(reg4p)
tab_model(reg5, reg4p)

```

```{r people intervention plot}
# how should we visualize this data?

g_people <- ggplot(d_intervention2,aes(y=people,x=age)) +
  geom_point() +
  geom_jitter() +
  geom_smooth(method="lm") +
  theme_minimal()

# plotting our data without reg lines
g_people

# You can make interactive plot easily with ggPredict() function included in ggiraphExtra package. this is me just messing around.
#library(ggiraphExtra)
#require(ggiraph)
#require(ggiraphExtra)
#require(plyr)
#ggPredict(reg1p,se=TRUE,interactive=TRUE)
#
#reg1p <- lm(people ~ age, data = d_intervention)
#summary(reg1p)
#tab_model(null_modelp, reg1p)
#
## creating a bar plot with our data, need to add error bars to this figure
#
#g_people1 <- ggplot(data=d_intervention, aes(x=age, y=people)) +
#  geom_bar(stat="identity", fill="purple")+
#  theme_minimal()
#
#g_people1
#
## not sure what this function does- need to check
#equation1p=function(x){coef(reg2p)[2]*x+coef(reg2p)[1]}
#equation2p=function(x){coef(reg2p)[2]*x+coef(reg2p)[1]+coef(reg2p)[3]}
#
#g_people2 <- ggplot(d_intervention,aes(y=people,x=age,color=gender)) + 
#        geom_point() +
#        stat_function(fun=equation1p,geom="line",color=scales::hue_pal()(2)[1]) +
#        stat_function(fun=equation2p,geom="line",color=scales::hue_pal()(2)[2]) +
#        theme_minimal()
#
#g_people2.1 <- g_people2 + geom_jitter(aes(color = gender), width = 0.5, height = 0.5)
#
#g_people2.2 <-g_people2.1 + labs(x = 'Age', y = 'God intervention score - People')
#
#g_people2.3 <- g_people2.2 + scale_color_discrete(labels=c('Male', 'Female'))
#
#g_people2.3
```

## Total intervention concepts all together

```{r total intervention regs}
# we start by creating our null model with a fixed slope and no predictors
null_modelt <- lm(totalinter ~ 1, data = d_intervention2)
summary(null_modelt)
tab_model(null_modelt)
coef(null_modelt)

reg1t <- lm(totalinter ~ age, data = d_intervention2)
summary(reg1t)
tab_model(null_modelt, reg1t)

reg2t <- lm(totalinter ~ age + gender, data = d_intervention2)
summary(reg2t)
tab_model(null_modelt, reg1t, reg2t)

reg3t <- lm(totalinter ~ age + gender + control + religiosity + age*gender + age*control + gender*control + age*religiosity + gender*religiosity + control*religiosity, data = d_intervention2)

reg4t <- lm(totalinter ~ age + gender + control + religiosity + age*control + gender*control, data = d_intervention2)


anova(reg4t)

AIC(reg1t, reg2t, reg3t, reg4t)

tab_model(reg5, reg4p, reg4t)


# we can see here that our second model is better (reg2)

```

```{r total intervention plot}
# how should we visualize this data?
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442")

g_environment <- ggplot(d_intervention2,aes(y=environment,x=age)) +
  geom_point() +
  geom_jitter() +
  geom_smooth(method="lm", color = "#E69F00") +
  theme_minimal()

# plotting our data without reg lines
g_environment

g_people <- ggplot(d_intervention2,aes(y=people,x=age)) +
  geom_point() +
  geom_jitter() +
  geom_smooth(method="lm", color = "#56B4E9") +
  theme_minimal()

# plotting our data without reg lines
g_people

g_total <- ggplot(d_intervention2,aes(y=totalinter,x=age)) +
  geom_point() +
  geom_jitter() +
  geom_smooth(method="lm", color = "#009E73") +
  theme_minimal()

# plotting our data without reg lines
g_total

#plotting regression lines on the same figure

#colors <- c("environment" = "#fdbf6f", "people" = "e2251d", "total" = "#fc9c9c")


g_allinter <- ggplot(d_intervention2, aes(x = age, y = totalinter)) + 
  geom_jitter(aes(age, environment, color = "Environment"), width = .2, height = .2, alpha=.4) +
  geom_smooth(aes(age,environment, color = "Environment"), method = "glm", se = FALSE) +
  geom_jitter(aes(age, people, color = "People"), width = .2, height = .2, alpha=.4) +
  geom_smooth(aes(age,people, color = "People"), method = "glm", se = FALSE) + 
  geom_jitter(aes(age, totalinter, color = "Total"), width = .2, height = .2, alpha=.4) +
  geom_smooth(aes(age,totalinter, color = "Total"), method = "glm", se = FALSE) +
  theme_minimal() +
  labs(title="Children's responses to intervention frequency questions by domain cluster", x = "Age", y = "Counts", color = "Domain") +
  theme(axis.text.x = element_text(angle=01)) +
  scale_color_manual(values = c("#fdbf6f", "#e2251d", "#fc9c9c"), name = "Domain")

g_allinter 

regpeople <- lm(people ~ age, data = d_intervention2)
summary(regpeople)

regenv <- lm(environment ~ age, data = d_intervention2)
summary(regenv)



```

```{r interventions altogether x gender bar figure}

d_intervention3 <- d_all %>% dplyr::select(starts_with("help_"), contains(c("helop_friends", "age", "gender")))

# recoding intervention colomns 
d_intervention3 <- d_intervention3 %>% 
  mutate_at(vars(1:14),
   ~as.numeric(dplyr::recode(.,
    "Never"=1,
    "Only at special times"=2,
    "Pretty often"=3,
    "Always"=4,
    "always" = 4,
    "IDK" = 5)))

# recoding gender here to use in our reg
d_intervention3$gender <- dplyr::recode(d_intervention3$gender, 'Male' = 1, 'Female'=2)

d_intervention3$gender <- as.factor(d_intervention3$gender)

#omitting NAs
d_intervention3 <- na.omit(d_intervention3)

#creating a filter to exclude IDK responses from analyses
d_intervention3 <- dplyr::filter(d_intervention3, help_plants != 5 | help_love != 5) 
d_intervention3 <- dplyr::filter(d_intervention3, help_love != 5) 

# let's convert our data to tall format so we can include all of the same plots on the same figure
library(reshape2)
d_intervention_reshaped <- melt(d_intervention3, id.vars= c("age", "gender"))

d_intervention_reshaped$value <- as.factor(d_intervention_reshaped$value)


# here, i'm making a dataframe with frequency counts added in
d_intervention_reshaped_counts <- table(d_intervention_reshaped$value, d_intervention_reshaped$variable, d_intervention_reshaped$gender)
addmargins(d_intervention_reshaped_counts)
round(prop.table(d_intervention_reshaped_counts,2)*100,digits=0)
df_irc <- as.data.frame(d_intervention_reshaped_counts)

# here, i'm making a dataframe with frequency counts added in
# d_intervention_reshaped_counts <- table(d_intervention_reshaped$value, d_intervention_reshaped$variable, d_intervention_reshaped$gender)
# addmargins(d_intervention_reshaped_counts)
# round(prop.table(d_intervention_reshaped_counts,2)*100,digits=0)
# df_irc <- as.data.frame(d_intervention_reshaped_counts)
# View(df_irc)
# creating our ggplot for all exist questions including both genders together. i'm labeling it p_exist because we're making a plot for the exist questions
p_irc <- ggplot(data = d_intervention_reshaped, aes(x = variable, y = age, fill = value)) +
       geom_bar(stat = "identity", width = .5) +
      theme_classic() +
      labs(title="Children's responses to God intervention frequency questions (14 items)", x ="Item", y = "Counts", fill = "Response") +
      theme(axis.text.x = element_text(angle=90))

# fixing the x axis labels
p_irc <- p_irc + scale_fill_discrete(labels=c("1" = "Never", "2" = "Only on special occasions", "3" = "Pretty often", "4" = "Always", "5" = "I don't know"))

# faceting by gender
# p_irc <- p_irc + facet_wrap(~Var3, ncol = 1) +
#     theme(panel.spacing = unit(1, "lines"))

p_irc

```

```{r something}
g_allinter <- g_allinter +
   labs(title="Figure 2. Predicted probabilities of interventionist frequency concepts across childhood", x = "Age", y = "Intervention frequency score", fill = "Response", color = "Response") +
  theme_minimal()

g_allinter
# running reg with just age
reg1t <- lm(people ~ age, data = d_intervention)
summary(reg1t)
tab_model(null_modelt, reg1t)

```

```{r comparing mean diffs between factors}
#making the daataframe long
longdata <- d_intervention2 %>% dplyr::select(starts_with("outcome"), starts_with("health"), starts_with("psych"), starts_with("social"), starts_with("environment"), starts_with("id_num")) 
longdata <- melt(longdata, id.vars= c("id_num"))

ggplot(data = longdata, mapping = aes(x = variable, y = value, color = variable)) + 
  geom_boxplot() +
  theme_minimal() +
  scale_color_brewer(palette= "Paired") +
  theme(legend.position = "none") +
  labs(title = "Intervention Cluster Mean Scores")


# Compute the analysis of variance
anova1 <- aov(value ~ variable, data = longdata)
# Summary of the analysis
summary(anova1)
TukeyHSD(anova1)

```

```{r correlation matrix for clusters}
#d_intervention2 <- d_intervention %>% dplyr::select(starts_with("help_"), contains(c("helop_friends")))
#
#d_intervention3 <- mutate_all(d_intervention2, function(d_intervention2) as.numeric(as.character(d_intervention2)))
#
#library(ggcorrplot)
#
#correlation_matrix <- round(cor(d_intervention3),1)
#corrp.mat <- cor_pmat(d_intervention3)
#ggcorrplot(correlation_matrix, method ="square",
#  hc.order = TRUE,
#  outline.color = "white",
#  type = "lower",
#  lab = TRUE,
#  insig = "blank",
#  colors = c("#ff7f00", "white", "#6a3d9a")) +
#  ggtitle("Correlation Matrix: All Intervention")

```


```