---
title: "cielo_manuscriptanalyses"
author: "Hannah Lunkenheimer"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(dev = "png",
                      dpi = 300,
                      echo = FALSE,
                      cache = TRUE)

packages <- c("moonBook", "dplyr", "readr", "ggplot2", "sjPlot", "apaTables", "lme4", "car", "DHARMa", "janitor", "reshape2", "ggsignif", "stats", "stringr", "ggpubr", "tidyr", "lsmeans", "daggity", "ggdag", "lsr") 

lapply(packages, require, character.only = TRUE)
```

```{r}
# load data
d_all <- read_csv("../data/data_clean/cielo_data.csv")
d_quotes <- read_csv("../data/data_raw/cielo_merged_raw.csv")
```

# Demographics

```{r demo}
# how many kids tested in person
table(d_all$online_in_person)

# how many kids tested in person
table(d_all$school)

# gender
table(d_all$gender)

# age
d_all %>%
  summarise(mean = mean(age),
            sd = sd(age))

# race
table(d_all$childs_race) 
table(d_all$childs_race_other) 

# ethnicity
table(d_all$childs_ethnicity)

# parent religion
table(d_all$relig_parent1)

# parent edu
parent_edu_bach <- d_all %>%
  filter(edu_parent1 == "bachelor's or 4 year degree" | edu_parent2 == "bachelor's or 4 year degree") %>%
  distinct()

```

Fig: Parent Religion Heatmap

```{r}
# make crosstab with parent religion
cross_tab <- table(d_all$relig_parent1, d_all$relig_parent2)

# turn tab into df
cross_tab_tidy <- as.data.frame.table(cross_tab)

# plot crosstab
relig_map <- ggplot(cross_tab_tidy, aes(x = Var1, y = Var2, size = Freq)) +
  geom_point(color = "#33a12c", shape = 21, fill = "#33a12c") +  
  scale_size_continuous(range = c(3, 10)) +
  geom_text(data = . %>% filter(Freq > 0), aes(label = Freq), color = "white", size = 3) +
  theme_minimal() +
  labs(x = "Parent 1 Religion", y = "Parent 2 Religion") +
  theme(axis.text.x = element_text(angle = 90),
        axis.text.y = element_text(angle = 0, hjust = 0.5),
        legend.position = "none") +
  scale_x_discrete(labels = function(x) str_to_title(x)) +
  scale_y_discrete(labels = function(y) str_to_title(y))

ggsave("../figs/relig_map.png", relig_map, width = 6, height = 4, dpi = 300)

```

# Results

Perceived control

```{r control}

table(d_all$control_cat)

d_control <- d_all %>%
  select(control_cat) %>%
  mutate(control_cat = as.factor(control_cat))

# chi square test, are there difference in perceived control?
bin_control <- d_control %>%
  mutate(control_cat = ifelse(control_cat == "control", 1, 0))

control_table <- table(bin_control)

chisq.test(control_table)

```
Family Influence

```{r}

# family religiosity
table(d_all$tradition_attend_service_freq)
table(d_all$tradition_importance)
d_all %>%
  select(fam_religiosity) %>%
  mutate(mean = mean(fam_religiosity, na.rm = TRUE),
         sd = sd(fam_religiosity, na.rm = TRUE))

# parent beliefs
table(d_all$intervention_parent_god)
table(d_all$intervention_parent_own_life)
d_all %>%
  select(parent_beliefs) %>%
  mutate(mean = mean(parent_beliefs, na.rm = TRUE),
         sd = sd(parent_beliefs, na.rm = TRUE))

```

Correlations

```{r general intervention framing}

d_framingcorr <- d_all %>% dplyr::select(contains(c("frame_can_make_happen_num", "frame_on_earth_num", "frame_peoples_lives_num", "frame_own_life_num")))

d_framingcorr <- d_framingcorr %>%
  filter(frame_can_make_happen_num != 3,
         frame_on_earth_num != 3,
         frame_peoples_lives_num != 3,
         frame_own_life_num != 3)

head(d_framingcorr)

tab_corr(d_framingcorr,
         p.numeric = TRUE,
         triangle = "lower")

```

```{r correlation parent beliefs and fam religiosity}

d_religcorr <- d_all %>% 
  select(tradition_attend_service_freq_num, tradition_importance_num, intervention_parent_god_num, intervention_parent_own_life_num)

d_religcorr <- na.omit(d_religcorr)

head(d_religcorr)

tab_corr(d_religcorr,
         p.numeric = TRUE,
         triangle = "lower")
```

```{r correlation bw intervention framing and domain intervention}

d_interventioncorr <- d_all %>% dplyr::select(framework_score, domain_score)

d_interventioncorr <- na.omit(d_interventioncorr)

head(d_interventioncorr)

tab_corr(d_interventioncorr,
         p.numeric = TRUE,
         triangle = "lower")

```

## Focal questions

```{r intervention framing model age}
#creating dataframe for intervention framing 
d_framing <- d_all %>% 
  select(frame_can_make_happen_num, frame_on_earth_num, 
         frame_peoples_lives_num, frame_own_life_num, age, 
         pid, control_cat, school, gender, fam_religiosity, 
         parent_beliefs, fam_influence, control, framework_score)
```

```{r}
d_personal <- d_all %>% 
  select(frame_can_make_happen_num, frame_on_earth_num, frame_peoples_lives_num, frame_own_life_num)

table(d_personal$frame_can_make_happen_num)
table(d_personal$frame_on_earth_num)
table(d_personal$frame_peoples_lives_num)
table(d_personal$frame_own_life_num)

# filtering out "idk" responses
filtered_data_noidk <- d_personal %>%
  filter(if_all(starts_with("frame"), ~ !is.na(.) & . != 3))

# pivot data longer
d_personal_long <- filtered_data_noidk %>%
  pivot_longer(cols = everything())

# run ANOVA to test for differences
anova_personal <- aov(value ~ name, data = d_personal_long)
summary(anova_personal)
etaSquared(anova_personal)
TukeyHSD(anova_personal)
```

## Possible Intervention Regressions

```{r framework possibility models}
d_framing_poss <- d_framing %>%
  filter(frame_can_make_happen_num != 3) 

# model 1
reg_dev_possibility <- glm(frame_can_make_happen_num ~ age, data = d_framing_poss, family = "binomial")
summary(reg_dev_possibility) 
# OR
coef_table <- coef(summary(reg_dev_possibility))
exp(coef_table[, "Estimate"])
exp(coef_table[, "Estimate"] - 1.96 * coef_table[, "Std. Error"]) # lower
exp(coef_table[, "Estimate"] + 1.96 * coef_table[, "Std. Error"]) # upper
AIC(reg_dev_possibility)

# model 2
reg_fr_possibility <- glm(frame_can_make_happen_num ~ fam_religiosity, data = d_framing_poss, family = "binomial")
summary(reg_fr_possibility) 
# OR
coef_table <- coef(summary(reg_fr_possibility))
exp(coef_table[, "Estimate"])
exp(coef_table[, "Estimate"] - 1.96 * coef_table[, "Std. Error"]) # lower
exp(coef_table[, "Estimate"] + 1.96 * coef_table[, "Std. Error"]) # upper
AIC(reg_fr_possibility)

# model 3
reg_pb_possibility <- glm(frame_can_make_happen_num ~ parent_beliefs + fam_religiosity, data = d_framing_poss, family = "binomial")
summary(reg_pb_possibility) 
# OR
coef_table <- coef(summary(reg_pb_possibility))
exp(coef_table[, "Estimate"])
exp(coef_table[, "Estimate"] - 1.96 * coef_table[, "Std. Error"]) # lower
exp(coef_table[, "Estimate"] + 1.96 * coef_table[, "Std. Error"]) # upper
AIC(reg_pb_possibility)

# model 4
reg_ctrl_possibility <- glm(frame_can_make_happen_num ~ control_cat + age, data = d_framing_poss, family = "binomial")
summary(reg_ctrl_possibility) 
# OR
coef_table <- coef(summary(reg_ctrl_possibility))
exp(coef_table[, "Estimate"])
exp(coef_table[, "Estimate"] - 1.96 * coef_table[, "Std. Error"]) # lower
exp(coef_table[, "Estimate"] + 1.96 * coef_table[, "Std. Error"]) # upper
AIC(reg_ctrl_possibility)

# model 5
reg_x1_possibility <- glm(frame_can_make_happen_num ~ age + fam_religiosity + age*fam_religiosity, data = d_framing_poss, family = "binomial")
summary(reg_x1_possibility) 
# OR
coef_table <- coef(summary(reg_x1_possibility))
exp(coef_table[, "Estimate"])
exp(coef_table[, "Estimate"] - 1.96 * coef_table[, "Std. Error"]) # lower
exp(coef_table[, "Estimate"] + 1.96 * coef_table[, "Std. Error"]) # upper
AIC(reg_x1_possibility)

# model 6
reg_x2_possibility <- glm(frame_can_make_happen_num ~ age + fam_religiosity + parent_beliefs + age*parent_beliefs, data = d_framing_poss, family = "binomial")
summary(reg_x2_possibility) 
# OR
coef_table <- coef(summary(reg_x2_possibility))
exp(coef_table[, "Estimate"])
exp(coef_table[, "Estimate"] - 1.96 * coef_table[, "Std. Error"]) # lower
exp(coef_table[, "Estimate"] + 1.96 * coef_table[, "Std. Error"]) # upper
AIC(reg_x2_possibility)

tab_model(reg_dev_possibility, 
          reg_fr_possibility, 
          reg_pb_possibility, 
          reg_ctrl_possibility, 
          reg_x1_possibility, 
          reg_x2_possibility, 
          show.est = TRUE,
          show.se = TRUE,
          show.ci = TRUE, 
          show.p = TRUE,
          show.r2 = TRUE,
          show.aic = TRUE)
```

## Actual Intervention: Earth

```{r framework on earth models}
d_framing_earth <- d_framing %>%
  filter(frame_on_earth_num != 3) 

reg_dev_earth <- glm(frame_on_earth_num ~ age, data = d_framing_earth, family = "binomial")
summary(reg_dev_earth)
AIC(reg_dev_earth)

reg_fr_earth <- glm(frame_on_earth_num ~ fam_religiosity, data = d_framing_earth, family = "binomial")
summary(reg_fr_earth)
AIC(reg_fr_earth)

reg_pb_earth <- glm(frame_on_earth_num ~ parent_beliefs + fam_religiosity, data = d_framing_earth, family = "binomial")
summary(reg_pb_earth)
AIC(reg_pb_earth)

reg_ctrl_earth <- glm(frame_on_earth_num ~ control_cat + age, data = d_framing_earth, family = "binomial")
summary(reg_ctrl_earth)
AIC(reg_ctrl_earth)

reg_x1_earth <- glm(frame_on_earth_num ~ age + fam_religiosity + age*fam_religiosity, data = d_framing_earth, family = "binomial")
summary(reg_x1_earth) 
AIC(reg_x1_earth)

reg_x2_earth <- glm(frame_on_earth_num ~ age + fam_religiosity + parent_beliefs + age*parent_beliefs, data = d_framing_earth, family = "binomial")
summary(reg_x2_earth) 
AIC(reg_x2_earth)

tab_model(reg_dev_earth, reg_fr_earth, reg_pb_earth, reg_ctrl_earth, reg_x1_earth, reg_x2_earth)

```

## Actual Intervention: People's lives

```{r framework on ppls lives models}
d_framing_ppl <- d_framing %>%
  filter(frame_peoples_lives_num != 3) 

reg_dev_ppl <- glm(frame_peoples_lives_num ~ age, data = d_framing_ppl, family = "binomial")
summary(reg_dev_ppl)

reg_fr_ppl <- glm(frame_peoples_lives_num ~ fam_religiosity, data = d_framing_ppl, family = "binomial")
summary(reg_fr_ppl)

reg_pb_ppl <- glm(frame_peoples_lives_num ~ parent_beliefs + fam_religiosity, data = d_framing_ppl, family = "binomial")
summary(reg_pb_ppl)

reg_ctrl_ppl <- glm(frame_peoples_lives_num ~ control + age, data = d_framing_ppl, family = "binomial")
summary(reg_ctrl_ppl)

reg_x1_ppl <- glm(frame_peoples_lives_num ~ age + fam_religiosity + age*fam_religiosity, data = d_framing_ppl, family = "binomial")
summary(reg_x1_ppl) 

reg_x2_ppl <- glm(frame_peoples_lives_num ~ age + fam_religiosity + parent_beliefs + age*parent_beliefs, data = d_framing_ppl, family = "binomial")
summary(reg_x2_ppl) 

tab_model(reg_pb_ppl)
```

## Actual Intervention: Own life

```{r framework on own life models}

d_framing_own <- d_framing %>%
  filter(frame_own_life_num != 3) 

reg_dev_ownlife <- glm(frame_own_life_num ~ age, data = d_framing_own, family = "binomial") 
summary(reg_dev_ownlife)

reg_fr_ownlife <- glm(frame_own_life_num ~ fam_religiosity, data = d_framing_own, family = "binomial")
summary(reg_fr_ownlife)

reg_pb_ownlife <- glm(frame_own_life_num ~ parent_beliefs + fam_religiosity, data = d_framing_own, family = "binomial")
summary(reg_pb_ownlife)

reg_ctrl_ownlife <- glm(frame_own_life_num ~ control_cat + age, data = d_framing_own, family = "binomial")
summary(reg_ctrl_ownlife)

reg_x1_ownlife <- glm(frame_own_life_num ~ age + fam_religiosity + age*fam_religiosity, data = d_framing_own, family = "binomial")
summary(reg_x1_ownlife) 

reg_x2_ownlife <- glm(frame_own_life_num ~ age + fam_religiosity + parent_beliefs + age*parent_beliefs, data = d_framing_own, family = "binomial")
summary(reg_x2_ownlife) 

tab_model(reg_x2_ownlife)
```

```{r other}
# ARE THERE DEVELOPMENTAL DIFFERENCES IN RESPONSES BY AGE? 
reg_dev_score <- lm(framework_score ~ age, data = d_framing)
summary(reg_dev_score)
```

```{r intervention framing model fr}

# DOES FAMILY RELIGIOSITY PREDICT INTERVENTION FRAMING SCORES? 
reg_fr_score <- lm(framework_score ~ fam_religiosity, data = d_framing)
summary(reg_fr_score)

```

```{r intervention framing model pb}

# DOES PARENT BELIEF PREDICT INTERVENTION FRAMING SCORES? 
reg_pb_score <- lm(framework_score ~ parent_beliefs + fam_religiosity, data = d_framing)
summary(reg_pb_score)
```

```{r intervention framing model pb}

# DOES FAMILY INFLUENCE LUMPED TOGETHER PREDICT INTERVENTION FRAMING?
reg_frame20 <- lm(framework_score ~ faminfluence, data = d_framing)
summary(reg_frame20)
reg_frame21 <- lm(frame_can_make_happen_num ~ faminfluence, data = d_framing)
summary(reg_frame21)
reg_frame22 <- lm(frame_on_earth_num ~ faminfluence, data = d_framing)
reg_frame23 <- lm(frame_peoples_lives_num ~ faminfluence, data = d_framing)
reg_frame24 <- lm(frame_own_life_num ~ faminfluence, data = d_framing)
tab_model(reg_frame20, reg_frame21, reg_frame22, reg_frame23, reg_frame24)




# DOES PERCEIVED CONTROL PREDICT INTERVENTION FRAMING SCORES? 
reg_frame3 <- lm(framework_score ~ control + age, data = d_framing)
summary(reg_frame3)

tab_model(reg_frame3, reg_frame3.1, reg_frame3.2, reg_frame3.3, reg_frame3.4)
reg_frame3.5 <- lm(framework_score ~ control*age, data = d_framing)
summary(reg_frame3.5)
reg_frame3.6 <- lm(framework_score ~ control*fam_religiosity, data = d_framing)
summary(reg_frame3.6)
reg_frame3.7 <- lm(framework_score ~ control*parent_beliefs, data = d_framing)
summary(reg_frame3.7)

# creating tables by question
tab_model(reg_frame4, reg_frame4.1, reg_frame4.2, reg_frame4.3, reg_frame4.4)

```


```{r summed scores for all vignette domains, echo=FALSE}
#creating dataframe for intervention framing fem
d_domains <- d_all %>% 
  select(control, age, pid, gender, fam_religiosity, parent_beliefs, (contains(c("domain_"))))

# ARE THERE DEVELOPMENTAL DIFFERENCES IN RESPONSES BY AGE FOR DOMAINS? 
reg_domain4 <- lm(domain_score ~ age, data = d_domains)
summary(reg_domain4)
reg_domain4.1 <- lm(domain_nature ~ age, data = d_domains)
summary(reg_domain4.1) 
reg_domain4.2 <- lm(domain_social ~ age, data = d_domains)
summary(reg_domain4.2)
reg_domain4.3 <- lm(domain_achieve ~ age, data = d_domains)
summary(reg_domain4.3)
reg_domain4.4 <- lm(domain_health ~ age, data = d_domains) 
summary(reg_domain4.4)
reg_domain4.5 <- lm(domain_psych ~ age, data = d_domains) 
summary(reg_domain4.5)
tab_model(reg_domain4, reg_domain4.1, reg_domain4.2, reg_domain4.3, reg_domain4.4, reg_domain4.5)

# DOES PERCEIVED CONTROL PREDICT INTERVENTION DOMAIN SCORES? 
reg_domain3 <- lm(alldomains ~ control + age, data = d_domains)
reg_domain_nature3 <- lm(environment ~ control + age, data = d_domains)
reg_domain_social3 <- lm(social ~ control + age, data = d_domains)
reg_domain_achieve3 <- lm(achieve ~ control + age, data = d_domains)
reg_domain_health3 <- lm(health ~ control + age, data = d_domains)
reg_domain_psych3 <- lm(psych ~ control + age, data = d_domains)

reg_domain_3.1 <- lm(alldomains ~ age*control, data = d_domains)
reg_domain_3.2 <- lm(alldomains ~ famreligiosity + parentbelief*control, data = d_domains)
reg_domain_3.3 <- lm(alldomains ~ famreligiosity*control, data = d_domains)
reg_domain_3.4 <- lm(alldomains ~ faminfluence*control, data = d_domains)

summary(reg_domain_3.1)
summary(reg_domain_3.2)
summary(reg_domain_3.3)
summary(reg_domain_3.4)

summary(reg_domain3)
# control doesn't predict any of the domains separately, either
summary(reg_domain_nature3)
summary(reg_domain_social3)
summary(reg_domain_achieve3)
summary(reg_domain_health3)
summary(reg_domain_psych3)

tab_model(reg_domain3, reg_domain_nature3, reg_domain_social3, reg_domain_achieve3, reg_domain_health3, reg_domain_psych3)

# DOES FAMILY RELIGIOSITY PREDICT INTERVENTION DOMAIN SCORES? 
reg_domain1 <- lm(alldomains ~ famreligiosity, data = d_domains)
reg_domain_nature1 <- lm(environment ~ famreligiosity, data = d_domains)
reg_domain_social1 <- lm(social ~ famreligiosity, data = d_domains)
reg_domain_psych1 <- lm(psych ~ famreligiosity, data = d_domains)
reg_domain_achieve1 <- lm(achieve ~ famreligiosity, data = d_domains)
reg_domain_health1 <- lm(health ~ famreligiosity, data = d_domains)
reg_domain1.1 <- lm(alldomains ~ famreligiosity*age, data = d_domains)

summary(reg_domain1)
summary(reg_domain1.1)
summary(reg_domain_nature1) 
summary(reg_domain_social1)
summary(reg_domain_psych1) #sig
summary(reg_domain_achieve1)
summary(reg_domain_health1) #sig
tab_model(reg_domain1, reg_domain_nature1, reg_domain_social1, reg_domain_achieve1, reg_domain_health1, reg_domain_psych1)

# DOES PARENT BELIEF PREDICT INTERVENTION DOMAIN SCORES? 
reg_domain2 <- lm(alldomains ~ parentbelief + famreligiosity, data = d_domains)
reg_domain_nature2 <- lm(environment ~ parentbelief + famreligiosity, data = d_domains)
reg_domain_social2 <- lm(social ~ parentbelief + famreligiosity, data = d_domains)
reg_domain_psych2 <- lm(psych ~ parentbelief + famreligiosity, data = d_domains)
reg_domain_achieve2 <- lm(achieve ~ parentbelief + famreligiosity, data = d_domains)
reg_domain_health2 <- lm(domain_health ~ parent_beliefs + fam_religiosity, data = d_domains)
reg_domain2.1 <- lm(alldomains ~ famreligiosity + age*parentbelief, data = d_domains)
summary(reg_domain2.1)
summary(reg_domain2)
summary(reg_domain_nature2)
summary(reg_domain_social2) #sig
summary(reg_domain_psych2)
summary(reg_domain_achieve2)
summary(reg_domain_health2) #sig

tab_model(reg_domain2, reg_domain_nature2, reg_domain_social2, reg_domain_psych2, reg_domain_achieve2, reg_domain_health2)

```


## All domains combined

```{r}
d_domain <- d_all %>% 
  select("age", "gender", "fam_influence", "fam_religiosity", "parent_beliefs", contains(c("pid", "domain", "control")))

domain_age_mod <- lm(domain_score ~ age, data = d_domain)
summary(domain_age_mod)

domain_famrelig_mod <- lm(domain_score ~ fam_religiosity, data = d_domain)
summary(domain_famrelig_mod)

domain_pb_mod <- lm(domain_score ~ parent_beliefs + fam_religiosity, data = d_domain)
summary(domain_pb_mod)

domain_control_mod <- lm(domain_score ~ age + control_cat, data = d_domain)
summary(domain_control_mod)

tab_model(domain_age_mod, domain_famrelig_mod, domain_pb_mod, domain_control_mod,
  show.est = TRUE,
  show.ci = 0.95,
  show.se = TRUE,
  std.response = TRUE,
  show.p = TRUE,
  show.loglik = TRUE)

```

## Nature domain
```{r nature domain}

nature_age_mod <- lm(domain_nature ~ age, data = d_domain)
summary(nature_age_mod)

nature_famrelig_mod <- lm(domain_nature ~ fam_religiosity, data = d_domain)
summary(nature_famrelig_mod)

nature_pb_mod <- lm(domain_nature ~ parent_beliefs + fam_religiosity, data = d_domain)
summary(nature_pb_mod)

nature_control_mod <- lm(domain_nature ~ age + control_cat, data = d_domain)
summary(nature_control_mod)

tab_model(nature_age_mod, nature_famrelig_mod, nature_pb_mod, nature_control_mod,
  show.est = TRUE,
  show.ci = 0.95,
  show.se = TRUE,
  std.response = TRUE,
  show.p = TRUE,
  show.loglik = TRUE)

```

## Achievement domain

```{r achievement domain}

achieve_age_mod <- lm(domain_achieve ~ age, data = d_domain)
summary(achieve_age_mod)

achieve_famrelig_mod <- lm(domain_achieve ~ fam_religiosity, data = d_domain)
summary(achieve_famrelig_mod)

achieve_pb_mod <- lm(domain_achieve ~ parent_beliefs + fam_religiosity, data = d_domain)
summary(achieve_pb_mod)

achieve_control_mod <- lm(domain_achieve ~ age + control_cat, data = d_domain)
summary(achieve_control_mod)

tab_model(achieve_age_mod, achieve_famrelig_mod, achieve_pb_mod, achieve_control_mod,
  show.est = TRUE,
  show.ci = 0.95,
  show.se = TRUE,
  std.response = TRUE,
  show.p = TRUE)
```

## Social domain

```{r social domain}

social_age_mod <- lm(domain_social ~ age, data = d_domain)
summary(social_age_mod)

social_famrelig_mod <- lm(domain_social ~ fam_religiosity, data = d_domain)
summary(social_famrelig_mod)

social_pb_mod <- lm(domain_social ~ parent_beliefs + fam_religiosity, data = d_domain)
summary(social_pb_mod)

social_control_mod <- lm(domain_social ~ age + control_cat, data = d_domain)
summary(social_control_mod)

tab_model(social_age_mod, social_famrelig_mod, social_pb_mod, social_control_mod,
  show.est = TRUE,
  show.ci = 0.95,
  show.se = TRUE,
  std.response = TRUE,
  show.p = TRUE)
```

## Psych domain

```{r psych domain}

psych_age_mod <- lm(domain_psych ~ age, data = d_domain)
summary(psych_age_mod)

psych_famrelig_mod <- lm(domain_psych ~ fam_religiosity, data = d_domain)
summary(psych_famrelig_mod)

psych_pb_mod <- lm(domain_psych ~ parent_beliefs + fam_religiosity, data = d_domain)
summary(psych_pb_mod)

psych_control_mod <- lm(domain_psych ~ age + control_cat, data = d_domain)
summary(psych_control_mod)

tab_model(psych_age_mod, psych_famrelig_mod, psych_pb_mod, psych_control_mod, 
  show.est = TRUE,
  show.ci = 0.95,
  show.se = TRUE,
  std.response = TRUE,
  show.p = TRUE)
```

## Health domain

```{r health domain}
health_age_mod <- lm(domain_health ~ age, data = d_domain)
summary(health_age_mod)

health_famrelig_mod <- lm(domain_health ~ fam_religiosity, data = d_domain)
summary(health_famrelig_mod)

health_pb_mod <- lm(domain_health ~ parent_beliefs + fam_religiosity, data = d_domain)
summary(health_pb_mod)

health_control_mod <- lm(domain_health ~ age + control_cat, data = d_domain)
summary(health_control_mod)

tab_model(health_age_mod, health_famrelig_mod, health_pb_mod, health_control_mod,
  show.est = TRUE,
  show.ci = 0.95,
  show.se = TRUE,
  std.response = TRUE,
  show.p = TRUE)
```

```{r looking at means diffs in domains}

d_domain2 <- d_all %>% 
  select(starts_with("domain"), pid)

d_domain2.2 <- d_domain2 %>% 
  select(-contains("_num"), pid, -domain_nature, -domain_psych, -domain_social, -domain_achieve, -domain_health, -domain_score)

d_domain_long2.2 <- melt(d_domain2.2, id.vars= c("pid"))

d_domain_long2.2 <- d_domain_long2.2 %>%
  mutate(variable = str_remove(variable, "domain_"),
         variable = str_remove(variable, "_num")) %>%
  separate(variable, into = c("category", "subcategory"), sep = "_")

d_domain_long3 <- d_domain_long2.2 %>%
  drop_na(value)

#d_domain_long3.2 <- d_domain_long2.2 %>%
#  drop_na(value)

subcategory_order <- c("sun", "seasons", "plants", "psych", "health")

d_domain_long3 <- d_domain_long3 %>%
  mutate(category = case_when(
    category == "health" ~ "Health",
    category == "social" ~ "Social",
    category == "psych" ~ "Psychological",
    category == "achieve" ~ "Achievement",
    category == "nature" ~ "Nature",
    TRUE ~ as.character(category)
  ))

domain_bar <- d_domain_long3 %>%
  mutate(value = factor(value, levels = c("never", "only at special times", "pretty often", "always")),
         category = factor(category, levels = c("Achievement", "Social", "Nature", 
                                                "Psychological", "Health")),
         subcategory = factor(subcategory, levels = c("sun", "seasons", "plants", 
                                                      "sports", "find", "school",
                                                      "love", "friends", 
                                                      "decisions", "dreams", "brave", "happier",
                                                      "sick", "safe"
                                                      ))) 

custom_palette <- c("#33a12c", "#b1df8a", "#a6cee3", "#1e78b5")

domain_bar <- domain_bar %>%
  ggplot(aes(x = subcategory, fill = value)) +  
  geom_bar() +
  theme_minimal() + 
  scale_fill_manual(values = custom_palette, labels = c("Never", "Only at special times", "Pretty often", "Always")) +  
  theme(legend.position = "bottom") +
  labs(title = "", x = "", y = "Count") + 
  scale_x_discrete(labels = c("sun" = "Sun", "seasons" = "Seasons", 
                               "plants" = "Plants", "love" = "Love", "friends" = "Friends",
                              "decisions" = "Decisions", "brave" = "Brave", "happier" = "Happier",
                              "sick" = "Sick", "safe" = "Safe", "sports" = "Sports", "find" = "Find",
                              "dreams" = "Dreams", "school" = "School")) +
  guides(fill = guide_legend(reverse = TRUE, title = NULL)) + 
  facet_grid(~category, scales = "free_x") 

domain_bar

ggsave("../figs/domain_bar.png", domain_bar, width = 12, height = 4, dpi = 300)

```


```{r}
d_domain_long <- d_all %>% 
  select(domain_psych, domain_achieve, domain_social, domain_health, domain_nature, age) %>%
  pivot_longer(cols = -age, names_to = "variable", values_to = "value") %>%
  mutate(variable = str_replace(variable, "domain_", ""))


d_domain_long$variable <- factor(d_domain_long$variable, levels = c("achieve", "social", "nature", "psych", "health"))

domain_clusters <- d_domain_long %>%
  filter(variable %in% c("achieve", "health", "psych", "social", "nature")) %>%
  ggplot(mapping = aes(x = variable, y = value, color = variable)) + 
    geom_violin() + 
    stat_summary(fun.y = mean, geom = "errorbar", aes(ymax = ..y.., ymin = ..y..),
                 width = .7 , size = 1, linetype = "solid") +
    stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2, size = 1) +
    geom_jitter(width = .3, height = 0, alpha=.3) +
    #geom_signif(comparisons = list(c("achieve", "health")), 
    #            y_position = 3.00,
    #            map_signif_level=TRUE,
    #            tip_length = 0,
    #            color = "black") +
    #geom_signif(comparisons = list(c("achieve", "psych")), 
    #           y_position = 3.25,
    #           map_signif_level=TRUE,
    #           tip_length = 0,
    #            color = "black") +
    #geom_signif(comparisons = list(c("achieve", "nature")), 
    #            y_position = 3.5,
    #            map_signif_level=TRUE,
    #            tip_length = 0,
    #            color = "black") +
    #geom_signif(comparisons = list(c("social", "health")), 
    #            y_position = 3.75,
    #            map_signif_level=TRUE,
    #            tip_length = 0,
    #            color = "black") +
    #geom_signif(comparisons = list(c("social", "psych")), 
    #            y_position =4,
    #            map_signif_level=TRUE,
    #            tip_length = 0,
    #            color = "black") +
    #geom_signif(comparisons = list(c("social", "nature")), 
    #            y_position =4.25,
    #            map_signif_level=TRUE,
    #            tip_length = 0,
    #            color = "black") +
    theme_minimal() +
    scale_color_brewer(palette= "Paired") +
    theme(legend.position = "none") +
    labs(title = "", x = "", y = "Domain Intervention Score") + 
    scale_x_discrete(labels=c("achieve" = "Achievement", 
                              "social" = "Social", 
                              "nature" = "Nature", 
                              "psych" = "Psychological", 
                              "health" = "Health")) +
    ylim(0, 3) 

domain_clusters

ggsave("../figs/domainclusters.png", domain_clusters, width = 5, height = 4, dpi = 300)

# Compute the analysis of variance
#anova1 <- aov(value ~ variable, data = d_domain_long)
# Summary of the analysis
#summary(anova1)
#TukeyHSD(anova1)

bartlett.test(value ~ variable, data = d_domain_long)

j1 <- lm(value ~ variable + age, data = d_domain_long) 

kruskal_test <- kruskal.test(value ~ variable, data = d_domain_long)


library(dunn.test)

# Perform the Dunn test
dunn_result <- dunn.test(d_domain_long$value, d_domain_long$variable, method = "bonferroni")
dunn_result


Anova(j1, type = 3) 

summary(j1)
# need to make pairwise tests
library(lsmeans)

tukey_result <- lsmeans(j1, "variable", adjust = "sidak")
print(tukey_result)

pairwise_comparisons <- pairs(tukey_result)
print(pairwise_comparisons)

```

```{r age differences in intervention by person nature and all domains}
#colors <- c("environment" = "#fdbf6f", "people" = "e2251d", "total" = "#fc9c9c")

g_allinter <- ggplot(d_domains, aes(x = age, domain_score)) + 
  geom_smooth(aes(x = age, y = domain_nature, color = "Nature"), method = "glm", se = FALSE) +
  geom_smooth(aes(age, domain_social, color = "Social"), method = "lm", se = FALSE) +
  geom_smooth(aes(age, domain_psych, color = "Psych"), method = "lm", se = FALSE) +
  geom_smooth(aes(age, domain_achieve, color = "Achieve"), method = "lm", se = FALSE) +
  geom_smooth(aes(age, domain_health, color = "Health"), method = "lm", se = FALSE) +
  theme_minimal() +
  scale_color_manual(values = c("#a6cfe3", "#2177b4", "#b7dd95", "#34a02b", "#fc9c9c"), name = "Domain",
                     limits = c("Achieve", "Social", "Nature", "Psych", "Health")) +
  ylim(0, 3) +
  labs(x = "Age",
       y = "Domain Intevention Score")

g_allinter

ggsave("../figs/g_allinter.png", g_allinter, width = 6, height = 4, dpi = 300)
# geom_jitter(aes(age, alldomains, color = "Total"), width = .2, height = .2, alpha=.4) +
# geom_smooth(aes(age, alldomains, color = "Total"), method = "glm", se = FALSE) +
```

## Child choice question

```{r child choice}
d_concepts <- d_all %>%
  select(framework_score, explicit_concepts, age, parent_beliefs, fam_religiosity, control_cat) %>%
  drop_na() %>%
  mutate(explicit_concepts = case_when(
    grepl("jordan", explicit_concepts, ignore.case = TRUE) ~ "3",
    grepl("riley", explicit_concepts, ignore.case = TRUE) ~ "0",
    grepl("sam", explicit_concepts, ignore.case = TRUE) ~ "1",
    TRUE ~ explicit_concepts  
  ))

table(d_all$explicit_concepts)

library(nnet)
model <- multinom(explicit_concepts ~ framework_score, data = d_concepts)

summary(model)

z <- summary(model)$coefficients/summary(model)$standard.errors
p <- (1 - pnorm(abs(z), 0, 1)) * 2
head(pp <- fitted(model))

lpp <- melt(d_concepts, id.vars = c("explicit_concepts"), value.name = "probability")
head(lpp)  # view first few rows

ggplot(lpp, aes(x = explicit_concepts, y = probability)) + 
  geom_line() + 
  facet_grid(variable ~
    ., scales = "free")

d_nojordan <- d_concepts %>%
  filter(explicit_concepts != "3") %>%
  mutate(explicit_concepts = as.numeric(explicit_concepts))

model <- glm(explicit_concepts ~ framework_score, data = d_nojordan, family = binomial)

# Summary of the model
summary(model)
# jordan who says god doesn't really make things happen in people's lives = 7
# riley, who says god makes things happen in people's lives at special times = 28
# sam, who says god makes things happen in people's lives almost every day = 41


m1 <- glm(explicit_concepts ~ age, data = d_nojordan, family = binomial)
summary(m1)

m2 <- glm(explicit_concepts ~ fam_religiosity, data = d_nojordan, family = binomial)
summary(m2)

m3 <- glm(explicit_concepts ~ parent_beliefs + fam_religiosity, data = d_nojordan, family = binomial)
summary(m3)

m4 <- glm(explicit_concepts ~ age + control_cat, data = d_nojordan, family = binomial)
summary(m4)
```

```{r multinomial logreg for child choice}
# we used nnet package to fit this type of reg
d_explicitconcepts <- d_all %>% dplyr::select("control", contains(c("age", "gender", "famreligiosity", "parentbelief", "explicit_concepts", "school", "alldomains")))

d_explicitconcepts <- na.omit(d_explicitconcepts)

d_explicitconcepts$explicit_concepts <- recode_factor(d_explicitconcepts$explicit_concepts, "Jordan, who says God doesn't really make things happen in people's lives." = "Jordan", "Riley, who says God makes things happen in people's lives, but only at special times." = "Riley", "Riley, who says God makes things happen in people's lives, but only special times." = "Riley", "Sam, who says God makes things happen in people's lives, almost every day." = "Sam")

d_explicitconcepts$explicit_concepts <- as.factor(d_explicitconcepts$explicit_concepts)

#lapply(split(d_explicitconcepts$explicit_concepts, travel$travel ), FUN=summary )

# loading the nnet package to run a multinomial model
library(nnet)

#note, r will automatically choose the lowest outcome category to be the referent group (jordan in this case)
mod_explicit <- multinom(explicit_concepts ~ parentbelief, data=d_explicitconcepts)
mod_explicitdomain <- multinom(explicit_concepts ~ alldomains, data=d_explicitconcepts)

#let's look at the outputs to summarize the data. turns out, they aren't so helpful for us. so, let's make a function below
mod_explicit
summary(mod_explicit)

summ.mod_explicit <- function( model ){
               s <- summary( model )
               for( i in 1:length(model$coef) ){
                         cat( "Level ", model$lev[i+1], "vs. Level ", model$lev[1] )
                         coef <- s$coefficients[i,]
                         rrr <- exp( coef )
                         se <- s$standard.errors[i,]
                         zStat <- coef / se
                         pVal <- 2*pnorm( abs(zStat), lower.tail=FALSE )
                         ci95.lo <- exp( coef - qnorm(.975)*se )
                         ci95.hi <- exp( coef + qnorm(.975)*se )
                         rslt <- cbind( rrr, se, zStat, pVal, ci95.lo, ci95.hi )
                         print( round( rslt, 3 ) )
                 }
}

# I tried running the function, but there was a comma after model$lev[1], ) why did this need to be removed to run?

#also, why did it only run 2 groups instead of 3?
summ.mod_explicit(mod_explicit)
#RRR = relative risk ratio

#so, is my conclusion that parent belief did not predict who children picked?

summ.mod_explicit(mod_explicitdomain)
```


```{r parent beliefs and age?}
ggplot(d_all, aes(x = age, y = alldomains)) +
  geom_smooth()

ggplot(d_all, aes(x = age, y = interview)) +
  geom_smooth()

ggplot(d_all, aes(x = interview, y = parentbelief)) +
  geom_smooth()

```

```{r looking at open-ended answers and age}

ggplot(d_all, aes(x = jw_codes, color = age)) +
  geom_bar()

d_rpers <- d_all %>% dplyr::select(contains(c("age", "jw_codes", "id_num")))

#d_openended$gender <- as.factor(d_openended$gender)

#omitting NAs
d_rpers <- na.omit(d_rpers)

# let's convert our data to tall format so we can include all of the same plots on the same figure
d_rpers_reshaped <- melt(d_rpers, id.vars= c("age", "id_num"))

d_rpers_reshaped$age <- as.factor(d_rpers_reshaped$age)

plot_rpers <- ggplot(data = d_rpers_reshaped, aes(x = value, fill = age)) +
      geom_bar() + 
      theme_classic() +
      labs(title="Children's responses to God interventionist framing questions", x ="Item", y = "Counts", fill = "Age") +
      theme(axis.text.x = element_text(angle=90))

# fixing the x axis labels
plot_rpers

# LOOKING AT PARENT BELIEFS
d_belief <- d_all %>% dplyr::select(contains(c("parentbelief", "jw_codes", "id_num")))

#d_openended$gender <- as.factor(d_openended$gender)

#omitting NAs
d_belief <- na.omit(d_belief)

# let's convert our data to tall format so we can include all of the same plots on the same figure
d_belief_reshaped <- melt(d_belief, id.vars= c("parentbelief", "id_num"))

d_belief_reshaped$parentbelief <- as.factor(d_belief_reshaped$parentbelief)

plot_d_belief_reshaped <- ggplot(data = d_belief_reshaped, aes(x = value, fill = parentbelief)) +
      geom_bar() + 
      theme_classic() +
      labs(title="Children's responses to God interventionist framing questions", x ="Item", y = "Counts", fill = "Parent belief") +
      theme(axis.text.x = element_text(angle=90))

# fixing the x axis labels
plot_d_belief_reshaped

```
