---
title: "intervention questionnaire analyses"
author: "Hannah Lunkenheimer"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(tidyverse)
library(sjPlot)
# to plot figs next to eachother
library(gridExtra)
library(ggsignif)
library(forcats)
library(jtools)
```

All subsequent framework analyses for the intervention framework task exclude participants who said "I don't know" or did not respond to the questions in the task.

```{r}
# reading in clean data
d_all <- read_csv("../data/data_clean/cielo_data.csv")

```
```{r anova focal questions}
# subset data to measure differences between focal questions
d_quest_anova <- d_all %>% dplyr::select("frame_can_make_happen_num", "frame_peoples_lives_num", "frame_own_life_num", "frame_on_earth_num")

# filtering out "na" responses
d_quest_anova2 <- na.omit(d_quest_anova)

#getting rid of "idks"
d_quest_anova3 <- d_quest_anova2 %>%
    filter(across(everything(), ~. != 0))

# pivot data to compare by question var
d_quest_anova_long <- d_quest_anova3 %>%
  pivot_longer(cols = everything())

# run anova
aov_frame <- aov(value ~ name, data = d_quest_anova_long)

# view results
summary(aov_frame)

# compare groups
TukeyHSD(aov_frame)

focalquestions <- ggplot(data = d_quest_anova_long, aes(x = value, y = name)) + 
  geom_jitter(aes(color = name), height = .3, width = .3) +
  scale_color_manual(limits = c("frame_can_make_happen_num", "frame_on_earth_num", "frame_peoples_lives_num", "frame_own_life_num"),
                    #labels = c("Can God...", "On Earth", "Own life", "People's lives"),
                    values = c("#E0462A", "#60CAD6", "#2A0C7A", "#DA7E68")) +
  labs(x = "Participant Responses", y = "Intervention interview:\nGeneral questions") +
  scale_x_discrete(limits = c(1, 2), labels = c("No", "Yes")) +
  scale_y_discrete(limits = c("frame_can_make_happen_num", "frame_on_earth_num", "frame_peoples_lives_num", "frame_own_life_num"), labels = c("Can God...?", "On Earth", "People's lives", "Own life")) +
  theme_minimal() +
  theme(legend.position = "bottom") 

focalquestions
ggsave("focalquestions_fig.png", focalquestions, width = 6, height = 5, dpi = 300)

```

```{r}
## selecting all of the columns that we need for our framework analysis
d_intervention <- d_all %>% 
  dplyr::select("age", "gender", "fam_influence", "fam_religiosity", "parent_beliefs", "framework_score", contains(c("pid", "frame_", "control")))
#

## renaming the framework score column to intervention_score
d_intervention <- d_intervention %>%
  rename(intervention_score = framework_score)

```

```{r}
# intervene altogether
quest_null_mod <- lm(intervention_score ~ 1, data = d_intervention)
summary(quest_null_mod)

quest_age_mod <- lm(intervention_score ~ age, data = d_intervention)
summary(quest_age_mod)

quest_famreg_mod <- lm(intervention_score ~ fam_religiosity, data = d_intervention)
summary(quest_famreg_mod)
tab_model(quest_famreg_mod)

quest_pb_mod <- lm(intervention_score ~ parent_beliefs + fam_religiosity, data = d_intervention)
summary(quest_pb_mod)

quest_control_mod <- lm(intervention_score ~ age + control_cat, data = d_intervention)
summary(quest_control_mod)
tab_model(quest_control_mod)
tab_model(quest_age_mod, quest_famreg_mod, quest_pb_mod, quest_control_mod)

```

```{r}
# interaction models
quest_famrelig_int_mod <- lm(intervention_score ~ age*fam_religiosity, data = d_intervention)
summary(quest_famrelig_int_mod)
tab_model(quest_famrelig_int_mod)

quest_pb_int_mod <- glm(intervention_score ~ age*parent_beliefs + fam_religiosity, data = d_intervention)
summary(quest_pb_int_mod)
tab_model(quest_pb_int_mod)

```

# Can God
```{r}
# let's look at whether god can intervene 

#omitting idk's from the dataset
d_can <- d_intervention %>%
  filter(frame_can_make_happen_num != 0) %>%
  mutate(frame_can_make_happen_bin = recode(frame_can_make_happen, "yes" = 1, "no" = 0))

can_null_mod <- glm(frame_can_make_happen_bin ~ 1, data = d_can, family = binomial)
summary(can_null_mod)

can_age_mod <- glm(frame_can_make_happen_bin ~ age, data = d_can, family = binomial)
summary(can_age_mod)

can_famreg_mod <- glm(frame_can_make_happen_bin ~ fam_religiosity, data = d_can)
summary(can_famreg_mod)

can_pb_mod <- glm(frame_can_make_happen_bin ~ parent_beliefs + fam_religiosity, data = d_can, family = binomial)
summary(can_pb_mod)

# control predicts can god
can_control_mod <- glm(frame_can_make_happen_bin ~ age + control_cat, data = d_can, family = binomial)
summary(can_control_mod)
tab_model(can_control_mod)

tab_model(can_age_mod, show.est = TRUE, p.style = "stars", show.aic = TRUE,   show.se = TRUE)
tab_model(can_famreg_mod, show.est = TRUE, p.style = "stars", show.aic = TRUE,   show.se = TRUE)
tab_model(can_pb_mod, show.est = TRUE, p.style = "stars", show.aic = TRUE,   show.se = TRUE)
tab_model(can_control_mod, show.est = TRUE, p.style = "stars", show.aic = TRUE,   show.se = TRUE)

```

```{r}
# interaction models
can_famrelig_int_mod <- glm(frame_can_make_happen_bin ~ age*fam_religiosity, family = binomial, data = d_can)
summary(can_famrelig_int_mod)
tab_model(can_famrelig_int_mod, show.est = TRUE, p.style = "stars", show.aic = TRUE,   show.se = TRUE)

can_pb_int_mod <- glm(frame_can_make_happen_bin ~ age*parent_beliefs + fam_religiosity, family = binomial, data = d_can)
summary(can_pb_int_mod)
tab_model(can_pb_int_mod, show.est = TRUE, p.style = "stars", show.aic = TRUE,   show.se = TRUE)

```

```{r}
# let's graph 
can_famrelig_plot <- ggplot(d_can, 
                   aes(x = age, 
                       y = frame_can_make_happen_num, 
                       color = as.factor(fam_religiosity))) + 
  geom_jitter(aes(age, frame_can_make_happen_num), 
              width = .1, height = .1, alpha=.3) +
  geom_smooth(aes(age, frame_can_make_happen_num), 
              method = "glm", se = FALSE) +
  scale_color_discrete() +
  labs(x = "Age", y = "Can God intervene on Earth, yes or no?", color = "Family Religiosity",
       title = "Interaction between Age\n and Family Religiosity") +
  theme_minimal() +
  theme(text = element_text(family = "Times New Roman"), legend.position = "bottom")


can_pb_plot <- ggplot(d_can, 
                   aes(x = age, 
                       y = frame_can_make_happen_num, 
                       color = as.factor(parent_beliefs))) + 
  geom_jitter(aes(age, frame_can_make_happen_num), 
              width = .1, height = .1, alpha=.3) +
  geom_smooth(aes(age, frame_can_make_happen_num), 
              method = "glm", se = FALSE) +
  scale_color_discrete() +
  labs(x = "Age", y = "Can God intervene on Earth, yes or no?", color = "Parent Intervention Beliefs",
       title = "Interaction between Age\n and Parent Intervention Beliefs") +
  theme_minimal() +
  theme(text = element_text(family = "Times New Roman"), legend.position = "bottom")

#grid.arrange(g_allinter, can_pb_plot, ncol = 1)

```

```{r}
# Calculate the count variable
d_can_summary <- d_all %>%
  group_by(frame_can_make_happen_num, control_cat) %>%
  summarise(count = n())

# Convert frame_can_make_happen_num to factor with custom labels
d_can_summary$frame_can_make_happen_num <- factor(d_can_summary$frame_can_make_happen_num,
                                                  levels = c(0, 1, 2),
                                                  labels = c("idk", "no", "yes"))

d_can_summary = na.omit(d_can_summary)


# Calculate proportions
d_can_proportions <- d_can_summary %>%
  group_by(frame_can_make_happen_num) %>%
  mutate(total_count = sum(count)) %>%
  ungroup() %>%
  mutate(proportion = count / total_count) %>%
  filter(frame_can_make_happen_num != "idk")

d_can_proportions_long <- d_can_proportions %>%
  select(-count, -total_count, -frame_can_make_happen_num) %>%
  mutate(control_cat = as.factor(control_cat),
         proportion = as.factor(proportion)) %>%
  pivot_longer(cols = -control_cat, names_to = "variable", values_to = "value")

# Create the plot
can_control_fig <- ggplot(d_can_proportions, aes(x = as.factor(frame_can_make_happen_num), y = proportion, fill = control_cat)) + 
  geom_bar(stat = "identity", position = "dodge") + 
  scale_fill_manual(values = "#E0462A", "#60CAD6", "#2A0C7A", "#DA7E68", name = "Control") + 
  labs(x = "Can God intervene on Earth, yes or no?", y = "Proportions", color = "Control",
       title = "Control") +
  geom_signif(comparisons = list(c("yes", "no")),
              map_signif_level=TRUE) +  
  theme_minimal()

# Convert proportion column to numeric
d_can_proportions$proportion <- as.numeric(d_can_proportions$proportion)

d_can_proportions$control_cat <- as.factor(d_can_proportions$control_cat)

# Create the plot
can_control_fig <- ggplot(d_can_proportions, aes(x = as.factor(frame_can_make_happen_num), 
                                                 y = proportion, fill = control_cat)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = c("#E0462A", "#60CAD6", "#2A0C7A", "#DA7E68"), 
                    name = "Perceived\ncontrol", labels = c("High", "Low")) +
  labs(x = "Can God intervene on Earth?", y = "Proportion of responses") +
    scale_x_discrete(labels = c("No", "Yes")) +
  theme_minimal() 

can_control_fig = can_control_fig + theme(legend.position = "right") 

ggsave("can_control_fig.png", can_control_fig, width = 4, height = 3.5, dpi = 300)

```

```{r}
#can_control_fig <- ggplot(d_can_proportions, aes(x = as.factor(frame_can_make_happen_num), 
#                                                 y = proportion, fill = control_cat)) +
#  geom_bar(stat = "identity", position = "dodge") +
#  scale_fill_manual(values = wes_palette("Royal2", n = 5), name = "Control") +
#  labs(x = "Can God intervene on Earth, yes or no?", y = "Proportions", color = "Control",
#       title = "Control") +
#  stat_compare_means(aes(label = p.signif), comparisons = list(c("yes", "no")),
#                     method = "t.test", ref.group = "no", map_signif_level = TRUE, 
#                     group.by = "control_cat") +
#  geom_signif(comparisons = list(
#    list(group1 = "yes", group2 = "no")
#  ), y_position = c(0.95, 0.9), tip_length = 0.02) +
#  theme_minimal()
#
#can_control_fig
#

control_int = c("no control, yes intervene", "no control, no intervene", "control, yes intervene", "control, no intervene")
count = c(94, 2, 35, 4)

#make into df
df = data.frame(control_int, count) 

#poisson
summary(glm(count ~ control_int, family=poisson))
```

Control predicts possibility of can God...

For our can God question, we have control as a significant predictor, and significant interactions of parent beliefs and age, and family religiosity and age. 

# On Earth
```{r}
# now let's look at God's intervention on Earth

#omitting idk's from the dataset
d_earth <- d_intervention %>%
  filter(frame_on_earth_num != 0) %>%
  mutate(frame_on_earth_bin = recode(frame_on_earth, "yes" = 1, "no" = 0))

# null model
earth_null_mod <- glm(frame_on_earth_bin ~ 1, family = binomial, data = d_earth)
summary(earth_null_mod)

earth_age_mod <- glm(frame_on_earth_bin ~ age, family = binomial, data = d_earth)
summary(earth_age_mod)

earth_famrelig_mod <- glm(frame_on_earth_bin ~ fam_religiosity, family = binomial, data = d_earth)
summary(earth_famrelig_mod)

earth_pb_mod <- glm(frame_on_earth_bin ~ parent_beliefs + fam_religiosity, family = binomial, data = d_earth)
summary(earth_pb_mod)

earth_control_mod <- glm(frame_on_earth_bin ~ age + control_cat, family = binomial, data = d_earth)
summary(earth_control_mod)

tab_model(earth_age_mod, earth_famrelig_mod, earth_pb_mod, earth_control_mod, show.est = TRUE, p.style = "stars", show.aic = TRUE,   show.se = TRUE)

```

```{r}
# interaction models
earth_famrelig_int_mod <- glm(frame_on_earth_bin ~ age*fam_religiosity, data = d_earth, family = binomial)
summary(earth_famrelig_int_mod)
coef(earth_famrelig_int_mod)
confint(earth_famrelig_int_mod, level = 0.95)
summary(earth_famrelig_int_mod)$coefficients[, "Std. Error"]
tab_model(earth_famrelig_int_mod, show.est = TRUE, p.style = "stars", show.aic = TRUE,   show.se = TRUE)

earth_pb_int_mod <- glm(frame_on_earth_bin ~ age*parent_beliefs + fam_religiosity, data = d_earth)
summary(earth_pb_int_mod)
tab_model(earth_pb_int_mod, show.est = TRUE, p.style = "stars", show.aic = TRUE,   show.se = TRUE)

```

```{r}
# let's graph 

earth_famrelig_plot <- ggplot(d_earth, 
                   aes(x = age, 
                       y = fam_religiosity, 
                       color = as.factor(frame_on_earth_num))) + 
  geom_jitter(aes(age, fam_religiosity), 
              width = .1, height = .1, alpha=.3) +
  geom_smooth(aes(age, fam_religiosity), 
              method = "glm", se = FALSE) +
  scale_color_discrete() +
  labs(x = "Age", y = "Fam Relig", color = "Answer",
       title = "Interaction between Age\n and Family Religiosity") +
  theme_minimal() +
  theme(text = element_text(family = "Times New Roman"), legend.position = "bottom")


earth_pb_plot <- ggplot(d_earth, 
                   aes(x = age, 
                       y = parent_beliefs, 
                       color = as.factor(frame_on_earth_num))) + 
  geom_jitter(aes(age, parent_beliefs), 
              width = .1, height = .1, alpha=.3) +
  geom_smooth(aes(age, parent_beliefs), 
              method = "glm", se = FALSE) +
  scale_color_discrete() +
  labs(x = "Age", y = "Parent beliefs", color = "Answer",
       title = "Interaction between Age\n and Parent Intervention Beliefs") +
  theme_minimal() +
  theme(text = element_text(family = "Times New Roman"), legend.position = "bottom")

grid.arrange(earth_famrelig_plot, earth_pb_plot, ncol = 2)

```
There is an interaction effect between age and religiosity that predicts intervention on Earth.

# People's lives
```{r}
# now let's look at personal intervention 

#omitting idk's from the dataset
d_people <- d_intervention %>%
  filter(frame_peoples_lives_num != 0) %>%
  mutate(frame_peoples_lives_bin = recode(frame_peoples_lives, "yes" = 1, "no" = 0))

# null model
people_null_mod <- glm(frame_peoples_lives_bin ~ 1, data = d_people, family = binomial)
summary(people_null_mod)

people_age_mod <- glm(frame_peoples_lives_bin ~ age, data = d_people, family = binomial)
summary(people_age_mod)

people_famrelig_mod <- glm(frame_peoples_lives_bin ~ fam_religiosity, data = d_people, family = binomial)
summary(people_famrelig_mod)

people_pb_mod <- glm(frame_peoples_lives_bin ~ parent_beliefs + fam_religiosity, data = d_people, family = binomial)
summary(people_pb_mod)
tab_model(people_pb_mod)

people_control_mod <- glm(frame_peoples_lives_bin ~ age + control_cat, data = d_people, family = binomial)
summary(people_control_mod)

tab_model(people_age_mod, people_famrelig_mod, people_pb_mod, people_control_mod, show.est = TRUE, p.style = "stars", show.aic = TRUE,   show.se = TRUE)

```

```{r}
# interaction models
people_famrelig_int_mod <- lm(frame_peoples_lives_bin ~ age*fam_religiosity, data = d_people)
summary(people_famrelig_int_mod)
AIC(people_famrelig_int_mod)

people_pb_int_mod <- lm(frame_peoples_lives_bin ~ age*parent_beliefs + fam_religiosity, data = d_people)
summary(people_pb_int_mod)
AIC(people_pb_int_mod)

tab_model(people_famrelig_int_mod, people_pb_int_mod, show.est = TRUE, p.style = "stars", show.aic = TRUE,   show.se = TRUE)
```

```{r}
# let's graph 
people_famrelig_plot <- ggplot(d_people, 
                   aes(x = age, 
                       y = frame_peoples_lives_num, 
                       color = as.factor(fam_religiosity))) + 
  geom_jitter(aes(age, frame_peoples_lives_num), 
              width = .1, height = .1, alpha=.3) +
  geom_smooth(aes(age, frame_peoples_lives_num), 
              method = "glm", se = FALSE) +
  scale_color_discrete() +
  labs(x = "Age", y = "Does God intervene in people's lives, yes or no?", color = "Family\n Religiosity",
       title = "Interaction between Age\n and Family Religiosity") +
  theme_minimal() +
  theme(text = element_text(family = "Times New Roman"), legend.position = "bottom")


people_pb_plot <- ggplot(d_people, 
                   aes(x = age, 
                       y = frame_peoples_lives_num, 
                       color = as.factor(parent_beliefs))) + 
  geom_jitter(aes(age, frame_peoples_lives_num), 
              width = .1, height = .1, alpha=.3) +
  geom_smooth(aes(age, frame_peoples_lives_num), 
              method = "glm", se = FALSE) +
  scale_color_discrete() +
  labs(x = "Age", y = "Does God intervene in people's lives, yes or no?", 
       color = "Parent\n Intervention\n Beliefs",
       title = "Interaction between Age\n and Parent Intervention Beliefs") +
  theme_minimal() +
  theme(text = element_text(family = "Times New Roman"), legend.position = "bottom")

grid.arrange(people_famrelig_plot, people_pb_plot, ncol = 2)

```

# Own life
```{r}
# now let's look at personal intervention 

#omitting idk's from the dataset
d_personal <- d_intervention %>%
  filter(frame_own_life_num != 0) %>%
  mutate(frame_own_life_bin = recode(frame_own_life, "yes" = 1, "no" = 0))

# null model
personal_null_mod <- lm(frame_own_life_bin ~ 1, data = d_personal)
summary(personal_null_mod)

personal_age_mod <- glm(frame_own_life_bin ~ age, data = d_personal, family = binomial)
summary(personal_age_mod)
tab_model(personal_age_mod)

personal_famrelig_mod <- lm(frame_own_life_bin ~ fam_religiosity, data = d_personal)
summary(personal_famrelig_mod)

personal_pb_mod <- lm(frame_own_life_bin ~ parent_beliefs + fam_religiosity, data = d_personal)
summary(personal_pb_mod)

personal_control_mod <- lm(frame_own_life_bin ~ age + control_cat, data = d_personal)
summary(personal_control_mod)

tab_model(personal_age_mod, personal_famrelig_mod, personal_pb_mod, personal_control_mod, show.est = TRUE, p.style = "stars", show.aic = TRUE,   show.se = TRUE)
#  show.est = TRUE,
#  show.ci = 0.95,
#  show.se = TRUE,
#  std.response = TRUE,
#  show.p = TRUE)
```

```{r}
# interaction models
personal_famrelig_int_mod <- lm(frame_own_life_bin ~ age*fam_religiosity, data = d_personal)
summary(personal_famrelig_int_mod)
AIC(personal_famrelig_int_mod)

personal_pb_int_mod <- lm(frame_own_life_bin ~ age*parent_beliefs + fam_religiosity, data = d_personal)
summary(personal_pb_int_mod)
AIC(personal_pb_int_mod)

tab_model(personal_famrelig_int_mod, personal_pb_int_mod, show.est = TRUE, p.style = "stars", show.aic = TRUE,   show.se = TRUE)
```

```{r}
# let's graph 
personal_famrelig_plot <- ggplot(d_personal, 
                   aes(x = age, 
                       y = frame_own_life_num, 
                       color = as.factor(fam_religiosity))) + 
  geom_jitter(aes(age, frame_own_life_num), 
              width = .1, height = .1, alpha=.3) +
  geom_smooth(aes(age, frame_own_life_num), 
              method = "glm", se = FALSE) +
  scale_color_discrete() +
  labs(x = "Age", y = "Has God intervened in your own life, yes or no?", color = "Family\n Religiosity",
       title = "Interaction between Age\n and Family Religiosity") +
  theme_minimal() +
  theme(text = element_text(family = "Times New Roman"), legend.position = "bottom")


personal_pb_plot <- ggplot(d_personal, 
                   aes(x = age, 
                       y = frame_own_life_num, 
                       color = as.factor(parent_beliefs))) + 
  geom_jitter(aes(age, frame_own_life_num), 
              width = .1, height = .1, alpha=.3) +
  geom_smooth(aes(age, frame_own_life_num), 
              method = "glm", se = FALSE) +
  scale_color_discrete() +
  labs(x = "Age", y = "Has God intervened in your own life, yes or no?", 
       color = "Parent\n Intervention\n Beliefs",
       title = "Interaction between Age\n and Parent Intervention Beliefs") +
  theme_minimal() +
  theme(text = element_text(family = "Times New Roman"), legend.position = "bottom")

grid.arrange(personal_famrelig_plot, personal_pb_plot, ncol = 2)

```
