---
title: "Cielo Analyses"
author: "Hannah Lunkenheimer"
date: "`r Sys.Date()`"
output: html_document
---

This is where the Woolley lab will run our analyses for the Cielo project. How fun! Our first group project in R and R Markdown.

R Markdown is a type of file (you can also have R scripts) that makes documents easy-ish to follow and organize your writing and/or analyses. 

Each Markdown file contains text like you see here, and code chunks. When we "knit" our RMD file to HTML, it will be formatted nicely because of these chunks.

First, we have our setup chunk, which is where we tell R what we want the output to look like when we knit. Include=FALSE in this chunk means that it will not be included in the knitted HTML file. Adding in echo=FALSE to the chunk means that when we knit the file, our code will not show, only the ouput. 

Anything that we include in the setup chunk will apply to all remaining chunks in the file, unless otherwise specified in a chunk.

In the setup chunk, we can load our packages.

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)

# loading packages

```

Next, depending where we're at in the process, we can use the remaining chunks in the file for data cleaning or analysis. If our data needs cleaning, we can do that here! Once we've finished our data cleaning, we can export the data as a new file in our R Project and call the cleaned data from another RMD file. 

```{r analysis}
# here is where we will load our data set

# is the data cleaned or do we need to do the cleaning?

# here is where we would recode any variables, fix mistakes, rename columns, etc

```

Adding #, ##, ###, #### etc in front of the text in the writing sections of the RMD file, it adds headings. 1 # is Heading 1, ## is heading 2, etc. When we knit the file, these headings will make it nice for our reader to follow what's going on in the script/process/plots/whatever! 

Also note, when we add our headers to the RMD file, there is an "Outline" column that is formed from your headers, making it easier to toggle between your files. 

## Some things to remember
- Googling your errors is 90% of trouble-shooting
- If you are unable to knit, check that your chunks all have different names!
- When you knit, the nice thing about RMD is that it tells you which line of code isn't working when you try and knit the file. Files will not knit if there is a problem with the code. 
- When we're finished working in a doc, we'll need to COMMIT our changes, and then PUSH them to our repo!
- Before we start working on a doc, we'll need to PULL the docs from our repo. 
- Always leave a helpful note of your changes in the commit box so we have a history of who did what
- R chunks can be minimized, which can help with cluttered files